---
title: "Analysis"
bibliography: references.bib
link-citations: true
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    toc_depth: 2
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide',message=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```



---  
  
# Getting started

To copy the code, click the button in the upper right corner of the code-chunks.

## clean up

```{r, eval=FALSE, results='hide'}
rm(list=ls())
gc()
```

<br>

## general custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R
- `fsave`: Function to save data with time stamp in correct directory
- `fload`: Function to load R-objects under new names
- `ftheme`: pretty ggplot2 theme
- `fshowdf`: Print objects (`tibble` / `data.frame`) nicely on screen in `.Rmd`.

```{r}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file, location = "./data/processed/", ...) {
    if (!dir.exists(location))
        dir.create(location)
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, datename, file, sep = "")
    print(paste("SAVED: ", totalname, sep = ""))
    save(x, file = totalname)
}

fload  <- function(fileName){
  load(fileName)
  get(ls()[ls() != "fileName"])
}

#extrafont::font_import(paths = c("C:/Users/u244147/Downloads/Jost/", prompt = FALSE))
ftheme <- function() {
  
  #download font at https://fonts.google.com/specimen/Jost/
  theme_minimal(base_family = "Jost") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "Jost", face = "bold"),
          axis.title = element_text(family = "Jost Medium"),
          axis.title.x = element_text(hjust = 0),
          axis.title.y = element_text(hjust = 1),
          strip.text = element_text(family = "Jost", face = "bold",
                                    size = rel(0.75), hjust = 0),
          strip.background = element_rect(fill = "grey90", color = NA),
          legend.position = "bottom")
}

fshowdf <- function(x, digits = 2, ...) {
    knitr::kable(x, digits = digits, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}
```

<br>


## necessary packages

- `tidyverse`
- `lme4`: fitting random effects models
- `lmtest`: diagnostics test (likelihood ratio test)
- `car`: companion applied regression (calculate VIF)
- `texreg`: output to HTML table


```{r, results='hide', message=FALSE, warning=FALSE}
packages = c("tidyverse", "lme4","lmtest","car","texreg")
fpackage.check(packages)
rm(packages)
``` 

<br>

## load data-set

Load the replicated data-set. To load these file, adjust the filename in the following code so that it matches the most recent version of the `.RDa` file you have in your `./data/processed/` folder.

You may also obtain them by downloading: `r xfun::embed_file("./data shared/netbehdata.Rda")`


```{r, results = 'hide'}
#list files in processed data folder
list.files("./data/processed/")

#get todays date:
today <- gsub("-", "", Sys.Date())

#use fload
df <- fload(paste0("./data/processed/", today, "netbehdata.Rda"))
```



<br>

# descriptives

```{r, des}
df$uni <- ifelse(df$education == "7", 1, 0)
df$ego_fitness_freq <- ifelse(df$ego_fitness > .99, 1, 0)

rbind(
  df %>%
  select(c("nfitp", "uni", "age", "female", "ego_fitness_freq", "nfitness", "nother")) %>%
  psych::describe(),
  df %>%
  filter(df$nfitp>0 & !is.na(df$avFreq)) %>%
  select(c("propFriend", "avFreq")) %>%
  psych::describe()
) -> table
row.names(table) <- c("no. of fitness partners", "research university student", "age in years", "female", "active in fitness ≥ 1 per week (baseline)", "total fitness sessions", "total other sports activities", "% best friends", "avg. fitness frequency alters")

table %>%
  select(-c(1,6,7,10:13)) %>%
  fshowdf()


```

<br>

  

# Regression

```{r, regression, eval = FALSE}
#full sample; effect of network size (0-5)
m1 <- lm(nfitness ~ nfitp, data = df )
summary(m1)

#include demographic controls:
m2 <- lm(nfitness ~ nfitp + uni + age + female, data = df )
summary(m2)

#also control for ego's fitness frequency at baseline (6 months before holiday): 1=once per week or more frequently; 0=less than once per week;

m3 <- lm(nfitness ~ nfitp + uni + age + female + ego_fitness_freq + nother, data = df )
summary(m3)

######################
#to study the effect of the composition of the network, we subset the respondents with at least one fitness partner
#composition measures for netsize==0 are 0 by design...

m4 <- lm(nfitness ~ nfitp, data = df[df$nfitp>0 & !is.na(df$avFreq),] )
summary(m4)

m5 <- lm(nfitness ~ nfitp + uni + age + female, data = df[df$nfitp>0 & !is.na(df$avFreq),])
summary(m5)

m6 <- lm(nfitness ~ nfitp + uni + age + female + ego_fitness_freq + nother, data = df[df$nfitp>0 & !is.na(df$avFreq),] )
summary(m6)

m7 <- lm(nfitness ~ nfitp + uni + age + female + ego_fitness_freq + nother + avFreq + propFriend, data = df[df$nfitp>0 & !is.na(df$avFreq),] )
summary(m7)
``` 

```{r, eval = FALSE, echo=FALSE}
?htmlreg
texreg::htmlreg(list(m1,m2,m3,m4,m5,m6,m7),
                file = "./results/coeftab.html",
                caption = "OLS regression effects on total fitness sessions",
                caption.above = TRUE,
                custom.coef.names = c("(Intercept)", "Network size", "Research university", "Age", "Female", "Fitness ≥ 1 per week (baseline)", "Frequency other activities", "Avg. Frequency alters", "Prop. Best friends"),
                reorder.coef = c(1,2,8,9,3,4,5,6,7),
        digits=2, single.row = TRUE
        )
``` 

```{r, echo = FALSE}
htmltools::tags$div(
  style = "height: 600px; overflow-y: scroll;",
  htmltools::includeHTML("./results/coeftab.html")
)
```
