---
title: "Data preparation"
bibliography: references.bib
link-citations: true
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    toc_depth: 2
    code_folding: show
    code_download: yes
---


```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide', message=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---  

The following scripts can be used to replicate the data-set of @Franken2023. It may also be obtained by downloading: `r xfun::embed_file("./data shared/netbeh_data.RDa")`



----

<br>

# Getting started

To copy the code, click the button in the upper right corner of the code-chunks.

## clean up

```{r clean, results='hide'}
rm(list=ls())
gc()
```

<br>

## general custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R
- `fsave`: Function to save data with time stamp in correct directory
- `fload`: Load R-objects under new names
- `fshowdf`: Print objects (`tibble` / `data.frame`) nicely on screen in `.Rmd`.

```{r custom_packages, eval=FALSE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file, location = "./data/processed/", ...) {
    if (!dir.exists(location))
        dir.create(location)
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, datename, file, sep = "")
    print(paste("SAVED: ", totalname, sep = ""))
    save(x, file = totalname)
}

fload  <- function(fileName){
  load(fileName)
  get(ls()[ls() != "fileName"])
}

fshowdf <- function(x, digits = 2, ...) {
    knitr::kable(x, digits = digits, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}
```

<br>

## necessary packages

- `dplyr`: package for data wrangling
- `lubridate`: parse and manipulate dates
- `stringr`: string manipulation

```{r packages, eval=FALSE}
packages = c("dplyr", "lubridate", "stringr")
fpackage.check(packages)
rm(list = setdiff(ls(), lsf.str()))
```
<br>

# Download data

Anonymized data-sets of the 'Sports and Friendships' study are deposited in DANS Data Station SSH [@data2022]. For this study we use waves 3-5 (Cohort II):

- `r xfun::embed_file("./data/wave3_public.RDa")`
- `r xfun::embed_file("./data/wave4_public.RDa")`
- `r xfun::embed_file("./data/wave5_public.RDa")`

Download the data-files, and put them in the `./data/` folder. But first, make a `./data/` folder: 

```{r, eval=FALSE}
ifelse(!dir.exists("data"), dir.create("data"), FALSE)
``` 

<br>

To see the code used to anonymize the raw data files, see: https://netchange.netlify.app/prep.


# Import data

Load the downloaded data. First, we clean our environment (but we keep our functions; we need them later on).

```{r, import, eval=FALSE}
#load public data
data3 <- fload("./data/wave3_public.RDa")
data4 <- fload("./data/wave4_public.RDa")
data5 <- fload("./data/wave5_public.RDa")
```


<br>

----

# Select fitness respondents

We select respondents who engaged in fitness:

- those who indicated participation in fitness during wave 1.
- those who weren't involved in fitness during wave 1 but listed it as an additional sports activity during wave 2.

```{r, select_respondent, eval=FALSE}
#get respnr of respondents who reported to have done fitness at w1
ids <- data3$respnr[which(data3$S1a.SQ001. == "Ja")]
#length(ids)/nrow(data3) #amounting to 63% of w1-respondents

#those who haven't been active in fitness during wave 1 can naturally begin their fitness journey by wave 2. In our survey, at w2, respondents were asked whether they still participated in the w1-listed sports types, and could list (at max) 3 additional sports types
#unique(cbind(data4$S1c.SQ001., data4$S1c.SQ002., data4$S1c.SQ003.)) 
#length(which(!data4$S1c.SQ001. == "")) / nrow(data4) #52% of w2-respondents did new sports type(s) compared to w1

#check which respondents reported fitness as new sports type;
#also synonyms are included (ignore case and leading and trailing spaces..)
inds <- which(apply(cbind(data4$S1c.SQ001., data4$S1c.SQ002., data4$S1c.SQ003.), 1, function(x) any(grepl("\\bfitness\\b|\\bkrachttraining\\b|\\bsportschool\\b", x, ignore.case = TRUE))))

#get respnr of these respondents
ids2 <- data4$respnr[inds]

#and also store in which entry (1-3) of the 'multiple open text' question, fitness was listed
#cbind(data4$S1c.SQ001., data4$S1c.SQ002., data4$S1c.SQ003.)[inds,]

fitness_entry <- apply(cbind(data4$S1c.SQ001., data4$S1c.SQ002., data4$S1c.SQ003.)[inds,], 1, function(x) {
  for (i in seq_along(x)) {
    if (any(grepl("\\bfitness\\b|\\bkrachttraining\\b|\\bsportschool\\b", x[i], ignore.case = TRUE))) {
      return(i)
      }
    }
  })

#store the ego ids (respnr) in a dataframe, specify whether fitness reported at w1 (as multiple choice answer) or w2 (as 'open entry'), and if in w2, in which entry. We will use this later to select the fitness sports partners of ego and to ultimately calculate (aggregate) network characteristics (e.g., structure, composition, stability) based on these alters.
w1 <- data.frame(respnr = ids, fitness = "w1")
w2 <- data.frame(respnr = ids2[which(!ids2 %in% ids)], fitness = "w2", fitness_entry = fitness_entry[which(!ids2 %in% ids)]) #no duplicates...

#bind
fitness_egos <- bind_rows(w1,w2)
fitness_egos <- fitness_egos[order(fitness_egos$respnr),]
rm(w1,w2,fitness_entry,ids,ids2,inds)

#subset data of these respondents
data3 <- data3[which(data3$respnr %in% fitness_egos$respnr),]
data4 <- data4[which(data4$respnr %in% fitness_egos$respnr),]
data5 <- data5[which(data5$respnr %in% fitness_egos$respnr),]
```

<br>

---

# Social network

I construct a long data-frame (based on Cohort II, waves 1-2-3), with alters nested in egos, to investigate which alters are maintained in the personal networks of ego over the academic year. To each ego, relevant individual-level, contextual-level, and network-level attributes are assigned; to each alter, relevant alter and dyadic features are assigned. The data-set is saved.


## wave 1 --> wave 2 (maintained vs dropped)

```{r, eval=FALSE}
# subset respondents that filled out both surveys w1 and w2 by matching on `respnr`
data <- data3[which(data3$respnr %in% unique(data4$respnr)),]
row.names(data) <- 1:nrow(data)
nrow(data) #N=370

# make a dataframe of w1-alters, with potential duplicates...
# recall that all alter names were replaced with a unique anonymized alter-id
df_names <- data.frame(
  p1 = data$egonet1.SQ001.,
  p2 = data$egonet1.SQ002.,
  p3 = data$egonet1.SQ003.,
  p4 = data$egonet1.SQ004.,
  p5 = data$egonet1.SQ005.,
  p6 = data$egonet2.SQ001.,
  p7 = data$egonet2.SQ002.,
  p8 = data$egonet2.SQ003.,
  p9 = data$egonet2.SQ004.,
  p10= data$egonet2.SQ005.,
  p11= data$egonet3.SQ001.,
  p12= data$egonet3.SQ002.,
  p13= data$egonet3.SQ003.,
  p14= data$egonet3.SQ004.,
  p15= data$egonet3.SQ005.,
  p16= data$egonet4.SQ001.,
  p17= data$egonet4.SQ002.,
  p18= data$egonet4.SQ003.,
  p19= data$egonet4.SQ004.,
  p20= data$egonet4.SQ005.)

#"pre-allocate" empty list of length equals number of egos
alterL <- vector("list", nrow(df_names))

# loop over all egos
for ( i in 1:length(alterL)) {
    alterL[[i]] <- data.frame(
      ego_gender = NA, ego_age = NA, ego_educ = NA,
      alterid = 1:20, name1 = NA, name2 = NA, name3 = NA, name4 = NA,
      alter_gender = NA, alter_age = NA, alter_educ=NA,
      same_gender = NA, dif_age = NA, sim_educ = NA)
}

# fill the names based on the names data-frame and replace empty strings with <NA>
for ( i in 1:length(alterL)) {
  alterL[[i]]$name1 <- unlist(df_names[i, ], use.names=FALSE)
  alterL[[i]]$name1 <- ifelse(alterL[[i]]$name1=="", NA, alterL[[i]]$name1)
}

# a matching matrix allowed ego to match names that referred to the same person.
# in limesurvey, i could not let the number of columns condition
# on the number of alters named in the latest egonet, so i made 5 separate matrices,
# conditional on netsize.
# i calculate netsize for each net
{
  net1 <- cbind(data$egonet1.SQ001.,data$egonet1.SQ002., data$egonet1.SQ003.,data$egonet1.SQ004., data$egonet1.SQ005.)
  net1 <- ifelse(net1=="", NA, net1)
  ns1 <- vector()
  for (i in 1:nrow(net1)) {
    ns1[i] <- length(net1[i,][which(!is.na(net1[i,]))])
  }
  net2 <- cbind(data$egonet2.SQ001.,data$egonet2.SQ002., data$egonet2.SQ003.,data$egonet2.SQ004., data$egonet2.SQ005.)
  net2 <- ifelse(net2=="", NA, net2)
  ns2 <- vector()
  for (i in 1:nrow(net2)) {
    ns2[i] <- length(net2[i,][which(!is.na(net2[i,]))])
  }
  net3 <- cbind(data$egonet3.SQ001.,data$egonet3.SQ002., data$egonet3.SQ003.,data$egonet3.SQ004., data$egonet3.SQ005.)
  net3 <- ifelse(net3=="", NA, net3)
  ns3 <- vector()
  for (i in 1:nrow(net3)) {
    ns3[i] <- length(net3[i,][which(!is.na(net3[i,]))])
  }
  net4 <- cbind(data$egonet4.SQ001.,data$egonet4.SQ002., data$egonet4.SQ003.,data$egonet4.SQ004., data$egonet4.SQ005.)
  net4 <- ifelse(net4=="", NA, net4)
  ns4 <- vector()
  for (i in 1:nrow(net4)) {
    ns4[i] <- length(net4[i,][which(!is.na(net4[i,]))])
  }
}

# i construct the matching matrices, 1 - 5 (conditional on the ns of the latest net)
# put these in a list and list these again, for each respondent (so a list of lists...)
matchingList <- list()
for (i in 1:length(alterL)) { # for ego i
  matchingL <- list()
  # make 5 seperate matching matrices. naturally, only 1 is relevant... but i will select that later.
  matchingL[[1]] <- cbind(data$matching1N1.SQ001_SQ001.[i],data$matching1N1.SQ002_SQ001.[i],data$matching1N1.SQ003_SQ001.[i],data$matching1N1.SQ004_SQ001.[i],data$matching1N1.SQ005_SQ001.[i])
  matchingL[[2]]<- rbind(
    cbind(data$matching1N2.SQ001_SQ001.[i], data$matching1N2.SQ002_SQ001.[i], data$matching1N2.SQ003_SQ001.[i], data$matching1N2.SQ004_SQ001.[i], data$matching1N2.SQ005_SQ001.[i]),
    cbind(data$matching1N2.SQ001_SQ002.[i], data$matching1N2.SQ002_SQ002.[i], data$matching1N2.SQ003_SQ002.[i], data$matching1N2.SQ004_SQ002.[i], data$matching1N2.SQ005_SQ002.[i]))
  matchingL[[3]]<- rbind(
    cbind(data$matching1N3.SQ001_SQ001.[i], data$matching1N3.SQ002_SQ001.[i], data$matching1N3.SQ003_SQ001.[i], data$matching1N3.SQ004_SQ001.[i], data$matching1N3.SQ005_SQ001.[i]),
    cbind(data$matching1N3.SQ001_SQ002.[i], data$matching1N3.SQ002_SQ002.[i], data$matching1N3.SQ003_SQ002.[i], data$matching1N3.SQ004_SQ002.[i], data$matching1N3.SQ005_SQ002.[i]),
    cbind(data$matching1N3.SQ001_SQ003.[i], data$matching1N3.SQ002_SQ003.[i], data$matching1N3.SQ003_SQ003.[i], data$matching1N3.SQ004_SQ003.[i], data$matching1N3.SQ005_SQ003.[i]))
  matchingL[[4]]<- rbind(
    cbind(data$matching1N4.SQ001_SQ001.[i], data$matching1N4.SQ002_SQ001.[i], data$matching1N4.SQ003_SQ001.[i], data$matching1N4.SQ004_SQ001.[i], data$matching1N4.SQ005_SQ001.[i]),
    cbind(data$matching1N4.SQ001_SQ002.[i], data$matching1N4.SQ002_SQ002.[i], data$matching1N4.SQ003_SQ002.[i], data$matching1N4.SQ004_SQ002.[i], data$matching1N4.SQ005_SQ002.[i]),
    cbind(data$matching1N4.SQ001_SQ003.[i], data$matching1N4.SQ002_SQ003.[i], data$matching1N4.SQ003_SQ003.[i], data$matching1N4.SQ004_SQ003.[i], data$matching1N4.SQ005_SQ003.[i]),
    cbind(data$matching1N4.SQ001_SQ004.[i], data$matching1N4.SQ002_SQ004.[i], data$matching1N4.SQ003_SQ004.[i], data$matching1N4.SQ004_SQ004.[i], data$matching1N4.SQ005_SQ004.[i]))
  matchingL[[5]]<- rbind(
    cbind(data$matching1N5.SQ001_SQ001.[i], data$matching1N5.SQ002_SQ001.[i], data$matching1N5.SQ003_SQ001.[i], data$matching1N5.SQ004_SQ001.[i], data$matching1N5.SQ005_SQ001.[i]),
    cbind(data$matching1N5.SQ001_SQ002.[i], data$matching1N5.SQ002_SQ002.[i], data$matching1N5.SQ003_SQ002.[i], data$matching1N5.SQ004_SQ002.[i], data$matching1N5.SQ005_SQ002.[i]),
    cbind(data$matching1N5.SQ001_SQ003.[i], data$matching1N5.SQ002_SQ003.[i], data$matching1N5.SQ003_SQ003.[i], data$matching1N5.SQ004_SQ003.[i], data$matching1N5.SQ005_SQ003.[i]),
    cbind(data$matching1N5.SQ001_SQ004.[i], data$matching1N5.SQ002_SQ004.[i], data$matching1N5.SQ003_SQ004.[i], data$matching1N5.SQ004_SQ004.[i], data$matching1N5.SQ005_SQ004.[i]),
    cbind(data$matching1N5.SQ001_SQ005.[i], data$matching1N5.SQ002_SQ005.[i], data$matching1N5.SQ003_SQ005.[i], data$matching1N5.SQ004_SQ005.[i], data$matching1N5.SQ005_SQ005.[i]))
  matchingList[[i]] <- matchingL
} # so... matchingL[[1]][[5]] is matchingmatrix 5 (i.e., 5 alters named in egonet2) for ego 1

# the combination of the matching matrices and the netsizes for ego allows me to match the names myself.
for (i in 1:length(matchingList)) {     # for ego i
  mL <- matchingList[[i]]               # get the matching list
  ns <- ns2[[i]]                        # get the size of egonet2
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # retrieve the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net2[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name2[which(alterL[[i]]$alterid==matched[,2])] <- net[matched[,1]]
    }
  }
} #ignore warning

#repeat for the second matching matrices
# (i.e., matching egonet3 alters to prev. alters);
matchingList2 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching2L <- list()
  matching2L[[1]] <- cbind(data$matching2N1.SQ001_SQ001.[i],data$matching2N1.SQ002_SQ001.[i],data$matching2N1.SQ003_SQ001.[i],data$matching2N1.SQ004_SQ001.[i],data$matching2N1.SQ005_SQ001.[i],data$matching2N1.SQ006_SQ001.[i],data$matching2N1.SQ007_SQ001.[i],data$matching2N1.SQ008_SQ001.[i],data$matching2N1.SQ009_SQ001.[i],data$matching2N1.SQ010_SQ001.[i])
  matching2L[[2]] <- rbind(
    cbind(data$matching2N2.SQ001_SQ001.[i],data$matching2N2.SQ002_SQ001.[i],data$matching2N2.SQ003_SQ001.[i],data$matching2N2.SQ004_SQ001.[i],data$matching2N2.SQ005_SQ001.[i],data$matching2N2.SQ006_SQ001.[i],data$matching2N2.SQ007_SQ001.[i],data$matching2N2.SQ008_SQ001.[i],data$matching2N2.SQ009_SQ001.[i],data$matching2N2.SQ010_SQ001.[i]),
    cbind(data$matching2N2.SQ001_SQ002.[i],data$matching2N2.SQ002_SQ002.[i],data$matching2N2.SQ003_SQ002.[i],data$matching2N2.SQ004_SQ002.[i],data$matching2N2.SQ005_SQ002.[i],data$matching2N2.SQ006_SQ002.[i],data$matching2N2.SQ007_SQ002.[i],data$matching2N2.SQ008_SQ002.[i],data$matching2N2.SQ009_SQ002.[i],data$matching2N2.SQ010_SQ002.[i]))
  matching2L[[3]] <- rbind(
    cbind(data$matching2N3.SQ001_SQ001.[i],data$matching2N3.SQ002_SQ001.[i],data$matching2N3.SQ003_SQ001.[i],data$matching2N3.SQ004_SQ001.[i],data$matching2N3.SQ005_SQ001.[i],data$matching2N3.SQ006_SQ001.[i],data$matching2N3.SQ007_SQ001.[i],data$matching2N3.SQ008_SQ001.[i],data$matching2N3.SQ009_SQ001.[i],data$matching2N3.SQ010_SQ001.[i]),
    cbind(data$matching2N3.SQ001_SQ002.[i],data$matching2N3.SQ002_SQ002.[i],data$matching2N3.SQ003_SQ002.[i],data$matching2N3.SQ004_SQ002.[i],data$matching2N3.SQ005_SQ002.[i],data$matching2N3.SQ006_SQ002.[i],data$matching2N3.SQ007_SQ002.[i],data$matching2N3.SQ008_SQ002.[i],data$matching2N3.SQ009_SQ002.[i],data$matching2N3.SQ010_SQ002.[i]),
    cbind(data$matching2N3.SQ001_SQ003.[i],data$matching2N3.SQ002_SQ003.[i],data$matching2N3.SQ003_SQ003.[i],data$matching2N3.SQ004_SQ003.[i],data$matching2N3.SQ005_SQ003.[i],data$matching2N3.SQ006_SQ003.[i],data$matching2N3.SQ007_SQ003.[i],data$matching2N3.SQ008_SQ003.[i],data$matching2N3.SQ009_SQ003.[i],data$matching2N3.SQ010_SQ003.[i]))
  matching2L[[4]] <- rbind(
    cbind(data$matching2N4.SQ001_SQ001.[i],data$matching2N4.SQ002_SQ001.[i],data$matching2N4.SQ003_SQ001.[i],data$matching2N4.SQ004_SQ001.[i],data$matching2N4.SQ005_SQ001.[i],data$matching2N4.SQ006_SQ001.[i],data$matching2N4.SQ007_SQ001.[i],data$matching2N4.SQ008_SQ001.[i],data$matching2N4.SQ009_SQ001.[i],data$matching2N4.SQ010_SQ001.[i]),
    cbind(data$matching2N4.SQ001_SQ002.[i],data$matching2N4.SQ002_SQ002.[i],data$matching2N4.SQ003_SQ002.[i],data$matching2N4.SQ004_SQ002.[i],data$matching2N4.SQ005_SQ002.[i],data$matching2N4.SQ006_SQ002.[i],data$matching2N4.SQ007_SQ002.[i],data$matching2N4.SQ008_SQ002.[i],data$matching2N4.SQ009_SQ002.[i],data$matching2N4.SQ010_SQ002.[i]),
    cbind(data$matching2N4.SQ001_SQ003.[i],data$matching2N4.SQ002_SQ003.[i],data$matching2N4.SQ003_SQ003.[i],data$matching2N4.SQ004_SQ003.[i],data$matching2N4.SQ005_SQ003.[i],data$matching2N4.SQ006_SQ003.[i],data$matching2N4.SQ007_SQ003.[i],data$matching2N4.SQ008_SQ003.[i],data$matching2N4.SQ009_SQ003.[i],data$matching2N4.SQ010_SQ003.[i]),
    cbind(data$matching2N4.SQ001_SQ004.[i],data$matching2N4.SQ002_SQ004.[i],data$matching2N4.SQ003_SQ004.[i],data$matching2N4.SQ004_SQ004.[i],data$matching2N4.SQ005_SQ004.[i],data$matching2N4.SQ006_SQ004.[i],data$matching2N4.SQ007_SQ004.[i],data$matching2N4.SQ008_SQ004.[i],data$matching2N4.SQ009_SQ004.[i],data$matching2N4.SQ010_SQ004.[i]))
  matching2L[[5]] <- rbind(
    cbind(data$matching2N5.SQ001_SQ001.[i],data$matching2N5.SQ002_SQ001.[i],data$matching2N5.SQ003_SQ001.[i],data$matching2N5.SQ004_SQ001.[i],data$matching2N5.SQ005_SQ001.[i],data$matching2N5.SQ006_SQ001.[i],data$matching2N5.SQ007_SQ001.[i],data$matching2N5.SQ008_SQ001.[i],data$matching2N5.SQ009_SQ001.[i],data$matching2N5.SQ010_SQ001.[i]),
    cbind(data$matching2N5.SQ001_SQ002.[i],data$matching2N5.SQ002_SQ002.[i],data$matching2N5.SQ003_SQ002.[i],data$matching2N5.SQ004_SQ002.[i],data$matching2N5.SQ005_SQ002.[i],data$matching2N5.SQ006_SQ002.[i],data$matching2N5.SQ007_SQ002.[i],data$matching2N5.SQ008_SQ002.[i],data$matching2N5.SQ009_SQ002.[i],data$matching2N5.SQ010_SQ002.[i]),
    cbind(data$matching2N5.SQ001_SQ003.[i],data$matching2N5.SQ002_SQ003.[i],data$matching2N5.SQ003_SQ003.[i],data$matching2N5.SQ004_SQ003.[i],data$matching2N5.SQ005_SQ003.[i],data$matching2N5.SQ006_SQ003.[i],data$matching2N5.SQ007_SQ003.[i],data$matching2N5.SQ008_SQ003.[i],data$matching2N5.SQ009_SQ003.[i],data$matching2N5.SQ010_SQ003.[i]),
    cbind(data$matching2N5.SQ001_SQ004.[i],data$matching2N5.SQ002_SQ004.[i],data$matching2N5.SQ003_SQ004.[i],data$matching2N5.SQ004_SQ004.[i],data$matching2N5.SQ005_SQ004.[i],data$matching2N5.SQ006_SQ004.[i],data$matching2N5.SQ007_SQ004.[i],data$matching2N5.SQ008_SQ004.[i],data$matching2N5.SQ009_SQ004.[i],data$matching2N5.SQ010_SQ004.[i]),
    cbind(data$matching2N5.SQ001_SQ005.[i],data$matching2N5.SQ002_SQ005.[i],data$matching2N5.SQ003_SQ005.[i],data$matching2N5.SQ004_SQ005.[i],data$matching2N5.SQ005_SQ005.[i],data$matching2N5.SQ006_SQ005.[i],data$matching2N5.SQ007_SQ005.[i],data$matching2N5.SQ008_SQ005.[i],data$matching2N5.SQ009_SQ005.[i],data$matching2N5.SQ010_SQ005.[i]))
  matchingList2[[i]] <- matching2L
}

for (i in 1:length(matchingList2)) {    # for ego i
  mL <- matchingList2[[i]]              # get the matching list 2
  ns <- ns3[[i]]                        # get the size of egonet3
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net3[i,]
    
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name3[matched[,2]] <- net[matched[,1]]
    }
  }
}

#and for matching matrix 3 (i.e., matching egonet4 with egonets 1-3)
matchingList3 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching3L <- list()
  matching3L[[1]] <- cbind(data$matching3N1.SQ001_SQ001.[i],data$matching3N1.SQ002_SQ001.[i],data$matching3N1.SQ003_SQ001.[i],data$matching3N1.SQ004_SQ001.[i],data$matching3N1.SQ005_SQ001.[i],data$matching3N1.SQ006_SQ001.[i],data$matching3N1.SQ007_SQ001.[i],data$matching3N1.SQ008_SQ001.[i],data$matching3N1.SQ009_SQ001.[i],data$matching3N1.SQ010_SQ001.[i], data$matching3N1.SQ011_SQ001.[i], data$matching3N1.SQ012_SQ001.[i], data$matching3N1.SQ013_SQ001.[i], data$matching3N1.SQ014_SQ001.[i], data$matching3N1.SQ015_SQ001.[i])
  matching3L[[2]] <- rbind(
    cbind(data$matching3N2.SQ001_SQ001.[i],data$matching3N2.SQ002_SQ001.[i],data$matching3N2.SQ003_SQ001.[i],data$matching3N2.SQ004_SQ001.[i],data$matching3N2.SQ005_SQ001.[i],data$matching3N2.SQ006_SQ001.[i],data$matching3N2.SQ007_SQ001.[i],data$matching3N2.SQ008_SQ001.[i],data$matching3N2.SQ009_SQ001.[i],data$matching3N2.SQ010_SQ001.[i], data$matching3N2.SQ011_SQ001.[i], data$matching3N2.SQ012_SQ001.[i], data$matching3N2.SQ013_SQ001.[i], data$matching3N2.SQ014_SQ001.[i], data$matching3N2.SQ015_SQ001.[i]),
    cbind(data$matching3N2.SQ001_SQ002.[i],data$matching3N2.SQ002_SQ002.[i],data$matching3N2.SQ003_SQ002.[i],data$matching3N2.SQ004_SQ002.[i],data$matching3N2.SQ005_SQ002.[i],data$matching3N2.SQ006_SQ002.[i],data$matching3N2.SQ007_SQ002.[i],data$matching3N2.SQ008_SQ002.[i],data$matching3N2.SQ009_SQ002.[i],data$matching3N2.SQ010_SQ002.[i], data$matching3N2.SQ011_SQ002.[i], data$matching3N2.SQ012_SQ002.[i], data$matching3N2.SQ013_SQ002.[i], data$matching3N2.SQ014_SQ002.[i], data$matching3N2.SQ015_SQ002.[i]))
  matching3L[[3]] <- rbind(
    cbind(data$matching3N3.SQ001_SQ001.[i],data$matching3N3.SQ002_SQ001.[i],data$matching3N3.SQ003_SQ001.[i],data$matching3N3.SQ004_SQ001.[i],data$matching3N3.SQ005_SQ001.[i],data$matching3N3.SQ006_SQ001.[i],data$matching3N3.SQ007_SQ001.[i],data$matching3N3.SQ008_SQ001.[i],data$matching3N3.SQ009_SQ001.[i],data$matching3N3.SQ010_SQ001.[i], data$matching3N3.SQ011_SQ001.[i], data$matching3N3.SQ012_SQ001.[i], data$matching3N3.SQ013_SQ001.[i], data$matching3N3.SQ014_SQ001.[i], data$matching3N3.SQ015_SQ001.[i]),
    cbind(data$matching3N3.SQ001_SQ002.[i],data$matching3N3.SQ002_SQ002.[i],data$matching3N3.SQ003_SQ002.[i],data$matching3N3.SQ004_SQ002.[i],data$matching3N3.SQ005_SQ002.[i],data$matching3N3.SQ006_SQ002.[i],data$matching3N3.SQ007_SQ002.[i],data$matching3N3.SQ008_SQ002.[i],data$matching3N3.SQ009_SQ002.[i],data$matching3N3.SQ010_SQ002.[i], data$matching3N3.SQ011_SQ002.[i], data$matching3N3.SQ012_SQ002.[i], data$matching3N3.SQ013_SQ002.[i], data$matching3N3.SQ014_SQ002.[i], data$matching3N3.SQ015_SQ002.[i]),
    cbind(data$matching3N3.SQ001_SQ003.[i],data$matching3N3.SQ002_SQ003.[i],data$matching3N3.SQ003_SQ003.[i],data$matching3N3.SQ004_SQ003.[i],data$matching3N3.SQ005_SQ003.[i],data$matching3N3.SQ006_SQ003.[i],data$matching3N3.SQ007_SQ003.[i],data$matching3N3.SQ008_SQ003.[i],data$matching3N3.SQ009_SQ003.[i],data$matching3N3.SQ010_SQ003.[i], data$matching3N3.SQ011_SQ003.[i], data$matching3N3.SQ012_SQ003.[i], data$matching3N3.SQ013_SQ003.[i], data$matching3N3.SQ014_SQ003.[i], data$matching3N3.SQ015_SQ003.[i]))
  matching3L[[4]] <- rbind(
    cbind(data$matching3N4.SQ001_SQ001.[i],data$matching3N4.SQ002_SQ001.[i],data$matching3N4.SQ003_SQ001.[i],data$matching3N4.SQ004_SQ001.[i],data$matching3N4.SQ005_SQ001.[i],data$matching3N4.SQ006_SQ001.[i],data$matching3N4.SQ007_SQ001.[i],data$matching3N4.SQ008_SQ001.[i],data$matching3N4.SQ009_SQ001.[i],data$matching3N4.SQ010_SQ001.[i], data$matching3N4.SQ011_SQ001.[i], data$matching3N4.SQ012_SQ001.[i], data$matching3N4.SQ013_SQ001.[i], data$matching3N4.SQ014_SQ001.[i], data$matching3N4.SQ015_SQ001.[i]),
    cbind(data$matching3N4.SQ001_SQ002.[i],data$matching3N4.SQ002_SQ002.[i],data$matching3N4.SQ003_SQ002.[i],data$matching3N4.SQ004_SQ002.[i],data$matching3N4.SQ005_SQ002.[i],data$matching3N4.SQ006_SQ002.[i],data$matching3N4.SQ007_SQ002.[i],data$matching3N4.SQ008_SQ002.[i],data$matching3N4.SQ009_SQ002.[i],data$matching3N4.SQ010_SQ002.[i], data$matching3N4.SQ011_SQ002.[i], data$matching3N4.SQ012_SQ002.[i], data$matching3N4.SQ013_SQ002.[i], data$matching3N4.SQ014_SQ002.[i], data$matching3N4.SQ015_SQ002.[i]),
    cbind(data$matching3N4.SQ001_SQ003.[i],data$matching3N4.SQ002_SQ003.[i],data$matching3N4.SQ003_SQ003.[i],data$matching3N4.SQ004_SQ003.[i],data$matching3N4.SQ005_SQ003.[i],data$matching3N4.SQ006_SQ003.[i],data$matching3N4.SQ007_SQ003.[i],data$matching3N4.SQ008_SQ003.[i],data$matching3N4.SQ009_SQ003.[i],data$matching3N4.SQ010_SQ003.[i], data$matching3N4.SQ011_SQ003.[i], data$matching3N4.SQ012_SQ003.[i], data$matching3N4.SQ013_SQ003.[i], data$matching3N4.SQ014_SQ003.[i], data$matching3N4.SQ015_SQ003.[i]),
    cbind(data$matching3N4.SQ001_SQ003.[i],data$matching3N4.SQ002_SQ003.[i],data$matching3N4.SQ003_SQ003.[i],data$matching3N4.SQ004_SQ003.[i],data$matching3N4.SQ005_SQ003.[i],data$matching3N4.SQ006_SQ003.[i],data$matching3N4.SQ007_SQ003.[i],data$matching3N4.SQ008_SQ003.[i],data$matching3N4.SQ009_SQ003.[i],data$matching3N4.SQ010_SQ003.[i], data$matching3N4.SQ011_SQ003.[i], data$matching3N4.SQ012_SQ003.[i], data$matching3N4.SQ013_SQ003.[i], data$matching3N4.SQ014_SQ003.[i], data$matching3N4.SQ015_SQ003.[i]),
    cbind(data$matching3N4.SQ001_SQ004.[i],data$matching3N4.SQ002_SQ004.[i],data$matching3N4.SQ003_SQ004.[i],data$matching3N4.SQ004_SQ004.[i],data$matching3N4.SQ005_SQ004.[i],data$matching3N4.SQ006_SQ004.[i],data$matching3N4.SQ007_SQ004.[i],data$matching3N4.SQ008_SQ004.[i],data$matching3N4.SQ009_SQ004.[i],data$matching3N4.SQ010_SQ004.[i], data$matching3N4.SQ011_SQ004.[i], data$matching3N4.SQ012_SQ004.[i], data$matching3N4.SQ013_SQ004.[i], data$matching3N4.SQ014_SQ004.[i], data$matching3N4.SQ015_SQ004.[i]))
  matching3L[[5]] <- rbind(
    cbind(data$matching3N5.SQ001_SQ001.[i],data$matching3N5.SQ002_SQ001.[i],data$matching3N5.SQ003_SQ001.[i],data$matching3N5.SQ004_SQ001.[i],data$matching3N5.SQ005_SQ001.[i],data$matching3N5.SQ006_SQ001.[i],data$matching3N5.SQ007_SQ001.[i],data$matching3N5.SQ008_SQ001.[i],data$matching3N5.SQ009_SQ001.[i],data$matching3N5.SQ010_SQ001.[i], data$matching3N5.SQ011_SQ001.[i], data$matching3N5.SQ012_SQ001.[i], data$matching3N5.SQ013_SQ001.[i], data$matching3N5.SQ014_SQ001.[i], data$matching3N5.SQ015_SQ001.[i]),
    cbind(data$matching3N5.SQ001_SQ002.[i],data$matching3N5.SQ002_SQ002.[i],data$matching3N5.SQ003_SQ002.[i],data$matching3N5.SQ004_SQ002.[i],data$matching3N5.SQ005_SQ002.[i],data$matching3N5.SQ006_SQ002.[i],data$matching3N5.SQ007_SQ002.[i],data$matching3N5.SQ008_SQ002.[i],data$matching3N5.SQ009_SQ002.[i],data$matching3N5.SQ010_SQ002.[i], data$matching3N5.SQ011_SQ002.[i], data$matching3N5.SQ012_SQ002.[i], data$matching3N5.SQ013_SQ002.[i], data$matching3N5.SQ014_SQ002.[i], data$matching3N5.SQ015_SQ002.[i]),
    cbind(data$matching3N5.SQ001_SQ003.[i],data$matching3N5.SQ002_SQ003.[i],data$matching3N5.SQ003_SQ003.[i],data$matching3N5.SQ004_SQ003.[i],data$matching3N5.SQ005_SQ003.[i],data$matching3N5.SQ006_SQ003.[i],data$matching3N5.SQ007_SQ003.[i],data$matching3N5.SQ008_SQ003.[i],data$matching3N5.SQ009_SQ003.[i],data$matching3N5.SQ010_SQ003.[i], data$matching3N5.SQ011_SQ003.[i], data$matching3N5.SQ012_SQ003.[i], data$matching3N5.SQ013_SQ003.[i], data$matching3N5.SQ014_SQ003.[i], data$matching3N5.SQ015_SQ003.[i]),
    cbind(data$matching3N5.SQ001_SQ003.[i],data$matching3N5.SQ002_SQ003.[i],data$matching3N5.SQ003_SQ003.[i],data$matching3N5.SQ004_SQ003.[i],data$matching3N5.SQ005_SQ003.[i],data$matching3N5.SQ006_SQ003.[i],data$matching3N5.SQ007_SQ003.[i],data$matching3N5.SQ008_SQ003.[i],data$matching3N5.SQ009_SQ003.[i],data$matching3N5.SQ010_SQ003.[i], data$matching3N5.SQ011_SQ003.[i], data$matching3N5.SQ012_SQ003.[i], data$matching3N5.SQ013_SQ003.[i], data$matching3N5.SQ014_SQ003.[i], data$matching3N5.SQ015_SQ003.[i]),
    cbind(data$matching3N5.SQ001_SQ005.[i],data$matching3N5.SQ002_SQ005.[i],data$matching3N5.SQ003_SQ005.[i],data$matching3N5.SQ004_SQ005.[i],data$matching3N5.SQ005_SQ005.[i],data$matching3N5.SQ006_SQ005.[i],data$matching3N5.SQ007_SQ005.[i],data$matching3N5.SQ008_SQ005.[i],data$matching3N5.SQ009_SQ005.[i],data$matching3N5.SQ010_SQ005.[i], data$matching3N5.SQ011_SQ005.[i], data$matching3N5.SQ012_SQ005.[i], data$matching3N5.SQ013_SQ005.[i], data$matching3N5.SQ014_SQ005.[i], data$matching3N5.SQ015_SQ005.[i]))
  matchingList3[[i]] <- matching3L
}

for (i in 1:length(matchingList3)) {    # for ego i
  mL <- matchingList3[[i]]              # get the matching list 2
  ns <- ns4[[i]]                        # get the size of egonet4
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net4[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name4[matched[,2]] <- net[matched[,1]]
    }
  }
}

# i use the name interpreter data to add (stable) alter characteristics (e.g., gender)
# in name-interpreter questions, only unique (i.e., non-matched) alters were listed... thus, alter ids without a gender assigned to them are non-uniques, and can later be filtered out.
df_gender <- data.frame(p1 = data$gender.SQ001.,p2 = data$gender.SQ002.,p3 = data$gender.SQ003.,p4 = data$gender.SQ004.,p5 = data$gender.SQ005.,p6 = data$gender.SQ006.,p7 = data$gender.SQ007.,p8 = data$gender.SQ008.,p9 = data$gender.SQ009.,p10= data$gender.SQ010.,p11= data$gender.SQ011.,p12= data$gender.SQ012.,p13= data$gender.SQ013.,p14= data$gender.SQ014.,p15= data$gender.SQ015.,p16= data$gender.SQ016.,p17= data$gender.SQ017.,p18= data$gender.SQ018.,p19= data$gender.SQ019.,p20= data$gender.SQ020.)

# same for age...
df_age <- data.frame(p1 = data$age.SQ001.,p2 = data$age.SQ002.,p3 = data$age.SQ003.,p4 = data$age.SQ004.,p5 = data$age.SQ005.,p6 = data$age.SQ006.,p7 = data$age.SQ007.,p8 = data$age.SQ008.,p9 = data$age.SQ009.,p10= data$age.SQ010.,p11= data$age.SQ011.,p12= data$age.SQ012.,p13= data$age.SQ013.,p14= data$age.SQ014.,p15= data$age.SQ015.,p16= data$age.SQ016.,p17= data$age.SQ017.,p18= data$age.SQ018.,p19= data$age.SQ019.,p20= data$age.SQ020.)

# kin
df_kin <- data.frame( p1 = data$kin.SQ001.,p2 = data$kin.SQ002.,p3 = data$kin.SQ003.,p4 = data$kin.SQ004.,p5 = data$kin.SQ005.,p6 = data$kin.SQ006.,p7 = data$kin.SQ007.,p8 = data$kin.SQ008.,p9 = data$kin.SQ009.,p10= data$kin.SQ010.,p11= data$kin.SQ011.,p12= data$kin.SQ012.,p13= data$kin.SQ013.,p14= data$kin.SQ014.,p15= data$kin.SQ015.,p16= data$kin.SQ016.,p17= data$kin.SQ017.,p18= data$kin.SQ018.,p19= data$kin.SQ019.,p20= data$kin.SQ020.)

#education
df_educ <- data.frame(p1 = data$educ.SQ001.,p2 = data$educ.SQ002.,p3 = data$educ.SQ003.,p4 = data$educ.SQ004.,p5 = data$educ.SQ005.,p6 = data$educ.SQ006.,p7 = data$educ.SQ007.,p8 = data$educ.SQ008., p9 = data$educ.SQ009.,p10= data$educ.SQ010., p11= data$educ.SQ011., p12= data$educ.SQ012., p13= data$educ.SQ013., p14= data$educ.SQ014., p15= data$educ.SQ015., p16= data$educ.SQ016., p17= data$educ.SQ017., p18= data$educ.SQ018., p19= data$educ.SQ019., p20= data$educ.SQ020.)

#also dynamic characteristics
#communication frequency
df_freq <- data.frame(p1 = data$freq.SQ001.,p2 = data$freq.SQ002.,p3 = data$freq.SQ003.,p4 = data$freq.SQ004.,p5 = data$freq.SQ005.,p6 = data$freq.SQ006.,p7 = data$freq.SQ007.,p8 = data$freq.SQ008., p9 = data$freq.SQ009.,p10= data$freq.SQ010., p11= data$freq.SQ011., p12= data$freq.SQ012., p13= data$freq.SQ013., p14= data$freq.SQ014., p15= data$freq.SQ015., p16= data$freq.SQ016., p17= data$freq.SQ017., p18= data$freq.SQ018., p19= data$freq.SQ019., p20= data$freq.SQ020.)

#closeness
df_close <- data.frame(p1 = data$close.SQ001.,p2 = data$close.SQ002.,p3 = data$close.SQ003.,p4 = data$close.SQ004.,p5 = data$close.SQ005.,p6 = data$close.SQ006.,p7 = data$close.SQ007.,p8 = data$close.SQ008., p9 = data$close.SQ009.,p10= data$close.SQ010., p11= data$close.SQ011., p12= data$close.SQ012., p13= data$close.SQ013., p14= data$close.SQ014., p15= data$close.SQ015., p16= data$close.SQ016., p17= data$close.SQ017., p18= data$close.SQ018., p19= data$close.SQ019., p20= data$close.SQ020.)

#and other dyadic featuers
# duration;
df_duration <- data.frame(p1 = data$duur.SQ001.,p2 = data$duur.SQ002.,p3 = data$duur.SQ003.,p4 = data$duur.SQ004.,p5 = data$duur.SQ005.,p6 = data$duur.SQ006.,p7 = data$duur.SQ007.,p8 = data$duur.SQ008., p9 = data$duur.SQ009.,p10= data$duur.SQ010., p11= data$duur.SQ011., p12= data$duur.SQ012., p13= data$duur.SQ013., p14= data$duur.SQ014., p15= data$duur.SQ015., p16= data$duur.SQ016., p17= data$duur.SQ017., p18= data$duur.SQ018., p19= data$duur.SQ019., p20= data$duur.SQ020.)

#geographical proximity
df_proximity <- data.frame(p1 = data$prox.SQ001.,p2 = data$prox.SQ002.,p3 = data$prox.SQ003.,p4 = data$prox.SQ004.,p5 = data$prox.SQ005.,p6 = data$prox.SQ006.,p7 = data$prox.SQ007.,p8 = data$prox.SQ008., p9 = data$prox.SQ009.,p10= data$prox.SQ010., p11= data$prox.SQ011., p12= data$prox.SQ012., p13= data$prox.SQ013., p14= data$prox.SQ014., p15= data$prox.SQ015., p16= data$prox.SQ016., p17= data$prox.SQ017., p18= data$prox.SQ018., p19= data$prox.SQ019., p20= data$prox.SQ020.)

for (i in 1:length(alterL)) {
  
  #gender
  alterL[[i]]$alter_gender <- 
    ifelse(unlist(df_gender[i,], use.names=F)=="Man", 0,  # male = ref.
           ifelse(unlist(df_gender[i,], use.names=F)=="Vrouw", 1,
                  ifelse(unlist(df_gender[i,], use.names=F)=="Anders", 2, "")))
  #kin  
  alterL[[i]]$kin <- 
    ifelse(unlist(df_kin[i,], use.names=F)=="Ja", 1,
           ifelse(unlist(df_kin[i,], use.names=F)=="Nee", 0, ""))
  #age  
  alterL[[i]]$alter_age <- 
    ifelse(unlist(df_age[i,], use.names=F)=="Jonger dan 18 jaar", 16, #???
           ifelse(unlist(df_age[i,], use.names=F)=="18 tot 21 jaar", 20,
                  ifelse(unlist(df_age[i,], use.names=F)=="22 tot 25 jaar", 23,
                         ifelse(unlist(df_age[i,], use.names=F)=="26 tot 30 jaar", 28,
                                ifelse(unlist(df_age[i,], use.names=F)=="31 tot 40 jaar", 35,
                                       ifelse(unlist(df_age[i,], use.names=F)=="Ouder dan 40 jaar", 45, #???
                                              ifelse(unlist(df_age[i,], use.names=F)=="Weet ik niet", NA, # i don't know = missing
                                                     unlist(df_age[i,], use.names=F))))))))
  #education
  alterL[[i]]$alter_educ <- ifelse(unlist(df_educ[i,],use.names=F)=="lagere school", 1,
                               ifelse(unlist(df_educ[i,],use.names=F)=="vmbo, mavo", 2,
                                      ifelse(unlist(df_educ[i,],use.names=F)=="mbo", 3,
                                         ifelse(unlist(df_educ[i,],use.names=F)=="havo", 4,
                                            ifelse(unlist(df_educ[i,],use.names=F)=="vwo / gymnasium", 5,
                                                 ifelse(unlist(df_educ[i,],use.names=F)=="hbo", 6,
                                                     ifelse(unlist(df_educ[i,],use.names=F)=="universiteit", 7, NA))))))) 
  #frequency
  alterL[[i]]$frequency.t1 <- ifelse(unlist(df_freq[i,],use.names=F)=="(Bijna) elke dag", 7,
                               ifelse(unlist(df_freq[i,],use.names=F)=="1-2 keer per week",6,
                                      ifelse(unlist(df_freq[i,],use.names=F)=="Aantal keer per maand",5, 
                                         ifelse(unlist(df_freq[i,],use.names=F)=="Ong. 1 keer per maand",4, 
                                            ifelse(unlist(df_freq[i,],use.names=F)=="Aantal keer per jaar",3,
                                                 ifelse(unlist(df_freq[i,],use.names=F)=="Ong. 1 keer per jaar",2,
                                                     ifelse(unlist(df_freq[i,],use.names=F)=="Nooit",1, NA )))))))
  #closeness
  alterL[[i]]$closeness.t1 <- ifelse(unlist(df_close[i,],use.names=F)=="Niet hecht", 1, 
                               ifelse(unlist(df_close[i,],use.names=F)=="Enigszins hecht", 2,
                                      ifelse(unlist(df_close[i,],use.names=F)=="Hecht", 3,
                                             ifelse(unlist(df_close[i,],use.names=F)=="Heel erg hecht", 4, NA ))))
  #proximity
  alterL[[i]]$proximity <- ifelse(unlist(df_proximity[i,], use.names=FALSE) == "In hetzelfde huis", "roommate",
                                  ifelse(unlist(df_proximity[i,], use.names = FALSE) == "In dezelfde buurt" |
                                    unlist(df_proximity[i,],use.names=F)=="In dezelfde straat" |
                                    unlist(df_proximity[i,],use.names=F)=="In dezelfde gemeente", "close",
                                    ifelse(unlist(df_proximity[i,], use.names = FALSE) == "In hetzelfde land" |
                                             unlist(df_proximity[i,], use.names = FALSE) == "In een ander land","far", NA)))

  
   #duration:  take midpoint on scale.
   alterL[[i]]$duration <- ifelse(unlist(df_duration[i,],use.names=F)=="Minder dan 1 jaar", 0, 
                               ifelse(unlist(df_duration[i,],use.names=F)=="1 tot 3 jaar", 2,
                                      ifelse(unlist(df_duration[i,],use.names=F)=="4 tot 8 jaar", 6,
                                             ifelse(unlist(df_duration[i,],use.names=F)=="9 tot 15 jaar", 12,
                                                    ifelse(unlist(df_duration[i,],use.names=F)=="Meer dan 15 jaar", 15,NA )))))
}

#for sports partners, how frequent they participate and how competent they are in the sport they do with ego.
df_altfreq <- data.frame(p1 = data$altfreq1, p2 = data$altfreq2, p3 = data$altfreq3, p4 = data$altfreq4, p5 = data$altfreq5)
df_altgrade <- data.frame(p1 = data$grade1, p2 = data$grade2, p3 = data$grade3, p4 = data$grade4, p5 = data$grade5)

for (i in 1:length(alterL)) { 
  alterL[[i]]$alter_freq[16:20] <- unlist(df_altfreq[i,], use.names=TRUE)
  alterL[[i]]$alter_grade[16:20] <- unlist(df_altgrade[i,], use.names=TRUE)
}

# before we can construct similarity indices, we must add ego-attributes
for (i in 1:length(alterL)) {
  #  gender
  alterL[[i]]$ego_gender <- ifelse(data$A1[i] == "Man", 0,ifelse(data$A1[i] == "Vrouw", 1,ifelse(data$A1[i] == "Overige", 2,NA)))
  
  # education 
  # these score should correspond to scores given to alter educ...
  alterL[[i]]$ego_educ <- ifelse(data$T1[i] == "aan de Hogeschool van Arnhem en Nijmegen (HAN)", "6", "7" )
 
  # age
  # calculated as the difference between submission date and birthdate
  # in years.
  birth_date <- as.Date(data$A2[i])
  #x_date <- as.Date(data$submitdate) #submission date was not deposited; so, take 1-jan 2023
  x_date <- as.Date("2023-01-01")
  alterL[[i]]$ego_age <- trunc((birth_date %--% x_date) / years(1))
}

# i also want to know ego's sports frequency and skill
# ultimately, i want to make a dyadic variable indicating the skill level (difference) of ego and alter, in *the specific sports that they do together*
# for now, i will put ego's sports frequency and skill, per sport, in a dataframe. 
# also, the setting ego participates each sports in (e.g., alone, informal, club-organized, ...)

#frequency
egos <- data %>%
  select(S3X.SQ001.:S3X.SQ017., S3bX.SQ001.:S3bX.SQ017. )
egos[egos == "Minder dan 1 keer per maand"] <- 0.125
egos[egos == "1 keer per maand" ] <- 0.25
egos[egos == "2 keer per maand" ] <- 0.5
egos[egos == "1 keer per week" ] <- 1

#in cases where ego participated more than once a week, get the answer to the questino how often per week he/she participated
for (i in 1:17) {
  egos[,i] <- ifelse(egos[,i] == "Vaker dan 1 keer per week", gsub("\\D", "", egos[,17+i]), egos[,i])
}
egos[,1:17] -> egos
egos <- mutate_all(egos, as.numeric)

#and skill
egos2 <- data %>%
  select(S2b.SQ001.: S2b.SQ017.)

#and setting
egos3 <- data %>%
  select(S2a.SQ001. : S2a.SQ017.)
egos3[egos3 == "Als lid van een commerciële sportaanbieder (bijv., fitnesscentrum)"] <- "gym"
egos3[egos3 == "Als lid van een sportvereniging"] <- "club"
egos3[egos3 == "In groepsverband, georganiseerd door jezelf, familie, vrienden, en/of kennissen"] <- "informal"
egos3[egos3 == "Alleen, ongeorganiseerd"] <- "alone"

# get for each sports partner in the list of alters, the sports ego does with them
for (i in 1:length(alterL)) { # for ego

  alterL[[i]]$sporttogether[16:20] <-
    
    c( ifelse( length(which( data[i,] %>%
  select(samenCSN1.SQ001.:samenCSN1.SQ017.) == "Ja" )) > 0,
  which(data[i,] %>% select(samenCSN1.SQ001.:samenCSN1.SQ017.) == "Ja" ), NA),
  
  ifelse( length(which( data[i,] %>%
  select(samenCSN2.SQ001.:samenCSN2.SQ017.) == "Ja" )) > 0,
  which(data[i,] %>% select(samenCSN2.SQ001.:samenCSN2.SQ017.) == "Ja" ), NA),
  
  ifelse( length(which( data[i,] %>%
  select(samenCSN3.SQ001.:samenCSN3.SQ017.) == "Ja" )) > 0,
  which(data[i,] %>% select(samenCSN3.SQ001.:samenCSN3.SQ017.) == "Ja" ), NA),
  
  ifelse( length(which( data[i,] %>%
  select(samenCSN4.SQ001.:samenCSN4.SQ017.) == "Ja" )) > 0,
  which(data[i,] %>% select(samenCSN4.SQ001.:samenCSN4.SQ017.) == "Ja" ), NA),
  
  ifelse( length(which( data[i,] %>%
  select(samenCSN5.SQ001.:samenCSN5.SQ017.) == "Ja" )) > 0,
  which(data[i,] %>% select(samenCSN5.SQ001.:samenCSN5.SQ017.) == "Ja" ), NA)
  )
}

# i filter out the unique, non-duplicate alters;
# by excluding alters with empty strings for gender attribute

#but first, match sports attributes.
#that is, from sports partners (p16-p20) to other alters who correspond to sports partners (name4)
for (i in 1:length(alterL)) {
  for (j in which(!is.na(alterL[[i]]$name4))) {
    alterL[[i]][j, c("alter_freq", "alter_grade", "sporttogether")] <- alterL[[i]][which(alterL[[i]]$name1 == alterL[[i]]$name4[j]), c("alter_freq", "alter_grade", "sporttogether")]
  }
}

#now do the filtering on gender, to filter out duplicates.
for ( i in 1:length(alterL)) {
  alterL[[i]] <- alterL[[i]][which(alterL[[i]]$alter_gender!=""),]
  # and replace the alter id: 1 : no. unique alters
  alterL[[i]]$alterid <- 1:nrow(alterL[[i]])
}

#attach ego_grade, ego's self-assessed skill for the sports he/she does together with alter
#and ego_freq, ego's sports frequency in this sports activity
#and ego_context, the social sporting context in which ego does this activity (assumedly, with alter)
for (i in 1:length(alterL)) { #for ego i
  alterL[[i]]$ego_grade <- NA
  alterL[[i]]$ego_freq <- NA
  alterL[[i]]$ego_context <- NA
  
  for (j in which(!is.na(alterL[[i]]$sporttogether))) { #for alters with a value on the 'sporttogether' attribute (i.e., who belong to sportnetwork)
    
    #attach ego's self-assessed sports skill for the sports he/she did with alter with alterid j
    alterL[[i]]$ego_grade[alterL[[i]]$alterid == j] <- egos2[i, alterL[[i]]$sporttogether[j]]
    
    #and ego's self-assessed sports frequency for this sports type
    alterL[[i]]$ego_freq[alterL[[i]]$alterid == j] <- egos[i, alterL[[i]]$sporttogether[j]]
    
    #and the setting in which ego engaged (with alter) in this sports type
    alterL[[i]]$ego_context[alterL[[i]]$alterid == j] <- egos3[i, alterL[[i]]$sporttogether[j]]
    
  }
}

#dyadic similarity measures
for (i in 1:length(alterL))  { # for ego i
  # get attributes of ego
  agei <- alterL[[i]]$ego_age[1]
  genderi <- alterL[[i]]$ego_gender[1]
  edi <- alterL[[i]]$ego_educ[1]
  
  for (j in 1:max(alterL[[i]]$alterid)) { # for alter j
    # calculate "same gender" (0/1)
    genderj <- as.numeric(alterL[[i]]$alter_gender[j]) # get alter j gender
    same <- ifelse(genderi==genderj, 1, 0)
    alterL[[i]]$same_gender[which(alterL[[i]]$alterid==j)] <- same
    
    #same education
    eduj <- alterL[[i]]$alter_educ[j]
    same <- ifelse(eduj==edi, 1, 0)
    alterL[[i]]$sim_educ[which(alterL[[i]]$alterid==j)] <- same
    
    # calculate similarity for age as the absolute difference between alter and ego value
    #get alter j attributes
    agej <- as.numeric(alterL[[i]]$alter_age[j])
    #difference score
    difage <- abs(agei - agej)
    
    # so higher values represent *less* similarity
    if( !is.na (agej) ) { # age similarity only calculable if z_j is known!
        alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- difage
      } else { alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- NA}
  }
}

#based on this, i make a long dataframe with alters nested in ego.
#first, add an ego_id
for (i in 1:length(alterL)) {
  alterL[[i]]$ego <- i
  alterL[[i]]$respnr <- data$respnr[i]
}

#combine using rbind
df <- do.call(rbind,alterL)

# add network variables
# 1. size (no. of unique alters)
df$netsize <- NA
# also per egonet
df$cdn.size <- df$study.size <- df$csn.size <- df$bff.size <- 0

for (i in unique(df$ego)) {
  #no. of unique alters is simply the number of rows per ego
  df$netsize[which(df$ego==i)] <- nrow(df[which(df$ego==i),])
  
  #size of each egonet is the number of alters named in the name generators
  #thus, including 'duplicates'
  df$cdn.size[which(df$ego==i)] <- length(which(!df_names[i,c(1:5)]==""))
  df$study.size[which(df$ego==i)] <- length(which(!df_names[i,c(6:10)]==""))
  df$bff.size[which(df$ego==i)] <- length(which(!df_names[i,c(11:15)]==""))
  df$csn.size[which(df$ego==i)] <- length(which(!df_names[i,c(16:20)]==""))
}

# 2. density.
# this can only be calculated per egonet, as only between-alter ties within egonet are asked.
df$cdn.density <- df$study.density <- df$csn.density <- df$bff.density <- NA

for (i in unique(df$ego)) {
  #a. CDN
  size <- df$cdn.size[which(df$ego==i)][1]
  #no. possible ties between alters
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  #get no. of observed ties
  #only if ego named at least 2 alters in this name generator
  #because only then i can calculate density
  if(size>1) {
    #get alter-alter adjacency matrices of this particular egonet
    adjacency <- data[i,c(13:32)]
   
    #i want the correct ones, given the no. of listed alters in this name generator
    #i list the columns numbers of the variables corresponding to each matching matrix set,
    #and subset corresponding columns in `adjacency`
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$cdn.density[which(df$ego==i)] <- obs/pos  }
  
  #b. study
  size <- df$study.size[which(df$ego==i)][1]
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  if(size>1) {
    adjacency <- data[i,c(53:72)]
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
  
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$study.density[which(df$ego==i)] <- obs/pos }
  
  #c. friends
  size <- df$bff.size[which(df$ego==i)][1]
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  if(size>1) {
    adjacency <- data[i,c(169:188)]
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$bff.density[which(df$ego==i)] <- obs/pos }

  #d. sports partners
  size <- df$csn.size[which(df$ego==i)][1]
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  if(size>1) {
    adjacency <- data[i,c(444:463)]

    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$csn.density[which(df$ego==i)] <- obs/pos }
}

#set NAs to 0.
df$cdn.density[is.na(df$cdn.density)] <- 0
df$study.density[is.na(df$study.density)] <- 0
df$bff.density[is.na(df$bff.density)] <- 0
df$csn.density[is.na(df$csn.density)] <- 0

#binary attributes indicating whether alters appeared in each of the ego-nets at w1.
for (i in unique(df$ego)) {   
    for (j in 1:nrow(df[which(df$ego==i),])) { # for alters nested in ego

    # find out if alter_id denoting alter j appear in the 4 egonets
    alter <- unlist(df[which(df$ego==i & df$alterid==j),][5:8], use.names = FALSE) # get name(s) of alter j
    alter <- alter[!is.na(alter)] # exclude NAs
    
    cdn <- alter %in% net1[i,]
    study <- alter %in% net2[i,]
    bff <- alter %in% net3[i,]
    csn <- alter %in% net4[i,]
    
    # and if so, give alter j score 1 on indicators; 0 otherwise
    df$cdn1[which(df$ego==i & df$alterid==j)] <- ifelse("TRUE" %in% cdn, 1, 0)
    df$study1[which(df$ego==i & df$alterid==j)] <- ifelse("TRUE" %in% study, 1, 0)
    df$bff1[which(df$ego==i & df$alterid==j)] <- ifelse("TRUE" %in% bff, 1, 0)
    df$csn1[which(df$ego==i & df$alterid==j)] <- ifelse("TRUE" %in% csn, 1, 0)
  }
}

#calculate multiplexity as an alter/tie attribute (i.e., number of *additional* networks j appeared in)
df$multiplex <- rowSums(df[,c(37:40)]) - 1 #minus one to reach a meaningful intercept

#now, find out whether w1-alters were maintainted in w2.
df$survive <- NA

# In wave 2, another matching procedure was used; in rows, alters named in w2 are listed; columns denote (unique) alters of w1, so the same one as our data-frame.
# again, i made multiple matrices, conditional on the no. of unique alters of w1 (15, to be precise)
# if, in one of these matrices, column j was marked as corresponding to a named alter in w2, then alter j did, indeed, survive

# subset w1-w2 matching matrices; and respnr
w1w2 <- data4[,c(756:1155,length(data4))]

for (i in unique(df$ego)) {  # for ego 
  matchingL <- vector("list", 20) #pre-allocate empty list of length 20, to store matching matrices

  {
    matchingL[[1]] <- w1w2[i,1:20]
    matchingL[[2]] <- w1w2[i,21:40]
    matchingL[[3]] <- w1w2[i,41:60]
    matchingL[[4]] <- w1w2[i,61:80]
    matchingL[[5]] <- w1w2[i,81:100]
    matchingL[[6]] <- w1w2[i,101:120]
    matchingL[[7]] <- w1w2[i,121:140]
    matchingL[[8]] <- w1w2[i,141:160]
    matchingL[[9]] <- w1w2[i,161:180]
    matchingL[[10]] <- w1w2[i,181:200]
    matchingL[[11]] <- w1w2[i,201:220]
    matchingL[[12]] <- w1w2[i,221:240]
    matchingL[[13]] <- w1w2[i,241:260]
    matchingL[[14]] <- w1w2[i,261:280]
    matchingL[[15]] <- w1w2[i,281:300]
    matchingL[[16]] <- w1w2[i,301:320]
    matchingL[[17]] <- w1w2[i,321:340]
    matchingL[[18]] <- w1w2[i,341:360]
    matchingL[[19]] <- w1w2[i,361:380]
    matchingL[[20]] <- w1w2[i,381:400]
  }
  
  #find the 'right' matching matrix in this list, by taking the one that contains answers
  ind <- NULL
  for (j in seq_along(matchingL)) {
    #check along the sequence of elements j in the matching matrix list if they are non-empty and not NA
    check <- FALSE
    for (col in matchingL[[j]]) {
      if (!all(is.na(col)) && any(nchar(col) > 0)) {
        check <- TRUE
        break  
      }
      }
    if (check) {
      ind <- j
      break  
    }
  }
  if(length(ind)>0) {
    # get the  corresponding matrix
    mm <- matchingL[[ind]]
    
    # unlist the answers given
    ans <- unlist(mm, use.names = FALSE)
    
    # use 'stringr' to extract numbers in these answers,
    # they refer to the id of "survived" alters
    id <- unlist(stringr::str_extract_all(ans,"\\(?[0-9,.]+\\)?"))
    id <- id[!is.na(id)] # exclude NA
    
    # if alter id of ego i corresponds to this id, they did indeed survive:
    df$survive[which(df$ego==i)] <- ifelse(df$alterid[which(df$ego==i)] %in% id, 1, 0)
  }
}

# in which egonet did they (re)appear?
df$cdn2 <- NA
df$study2 <- NA
df$bff2 <- NA
df$csn2 <- NA

# i use the matching matrices of w2; where columns refer to unique w1-alters (those of our constructed data-frame) and rows referring to unique w2 alters
# so, if w1-alter/column j is matched to w2-alter/row i, then w1-alter did survive (but we already knew that); but more importantly, j was the i^th alter mentioned
# and this allows me to infer in what network j (re-)appeared
# since cdn = 1-5; study = 6-10; bff = 11-15; csn = 16-20.
# however, since the rows only include non-duplicate w2-alters;
# if alter j at t1 was named more than once at t2, i only know the first
# egonet in which j was named...
# thus, before i proceed, i use the matching matrices that allowed ego to match alters from different egonets to make alter ids for w2 alters; and figure out to which egonets they belonged

# i make a dataframe of w2-alters, with potential duplicates...
df_names <- data.frame(p1 = data4$egonet1.SQ001.,p2 = data4$egonet1.SQ002.,p3 = data4$egonet1.SQ003.,p4 = data4$egonet1.SQ004.,p5 = data4$egonet1.SQ005.,p6 = data4$egonet2.SQ001.,p7 = data4$egonet2.SQ002.,p8 = data4$egonet2.SQ003.,p9 = data4$egonet2.SQ004.,p10= data4$egonet2.SQ005.,p11= data4$egonet3.SQ001.,p12= data4$egonet3.SQ002.,p13= data4$egonet3.SQ003.,p14= data4$egonet3.SQ004.,p15= data4$egonet3.SQ005.,p16= data4$egonet4.SQ001., p17= data4$egonet4.SQ002., p18= data4$egonet4.SQ003.,p19= data4$egonet4.SQ004.,p20= data4$egonet4.SQ005.)

#males
df_gender <- data.frame(p1 = data4$males.SQ001.,p2 = data4$males.SQ002.,p3 = data4$males.SQ003.,p4 = data4$males.SQ004.,p5 = data4$males.SQ005.,p6 = data4$males.SQ006.,p7 = data4$males.SQ007.,p8 = data4$males.SQ008.,p9 = data4$males.SQ009.,p10= data4$males.SQ010.,p11= data4$males.SQ011.,p12= data4$males.SQ012.,p13= data4$males.SQ013.,p14= data4$males.SQ014.,p15= data4$males.SQ015.,p16= data4$males.SQ016.,p17= data4$males.SQ017.,p18= data4$males.SQ018.,p19= data4$males.SQ019.,p20= data4$males.SQ020.)

# list of dataframes per ego with rows reflecting alters
# and columns indicating the name(s) of the particular alters
alterL <- list()
# loop over all egos
for ( i in 1:nrow(df_names)) {alterL[[i]] <- data.frame(
    alterid = 1:20,name1 = NA,name2 = NA, name3 = NA,name4 = NA, gender=NA)}

# fill the names based on the names data-frame
for ( i in 1:length(alterL)) {
  alterL[[i]]$name1 <- unlist(df_names[i, ], use.names=F)
  alterL[[i]]$name1 <- ifelse(alterL[[i]]$name1=="", NA, alterL[[i]]$name1)
  
  alterL[[i]]$gender <- unlist(df_gender[i,], use.names=F)
  alterL[[i]]$gender <- ifelse(alterL[[i]]$gender=="Ja", 0, #male = ref
                               ifelse(alterL[[i]]$gender=="Nee", 1, NA))
  
  }

# calculate netsize for each net to get the correct matching matrix
{
  net1 <- cbind(data4$egonet1.SQ001.,data4$egonet1.SQ002., data4$egonet1.SQ003.,data4$egonet1.SQ004., data4$egonet1.SQ005.)
  net1 <- ifelse(net1=="", NA, net1)
  ns1 <- vector()
  for (i in 1:nrow(net1)) {
    ns1[i] <- length(net1[i,][which(!is.na(net1[i,]))])
  }
  net2 <- cbind(data4$egonet2.SQ001.,data4$egonet2.SQ002., data4$egonet2.SQ003.,data4$egonet2.SQ004., data4$egonet2.SQ005.)
  net2 <- ifelse(net2=="", NA, net2)
  ns2 <- vector()
  for (i in 1:nrow(net2)) {
    ns2[i] <- length(net2[i,][which(!is.na(net2[i,]))])
  }
  net3 <- cbind(data4$egonet3.SQ001.,data4$egonet3.SQ002., data4$egonet3.SQ003.,data4$egonet3.SQ004., data4$egonet3.SQ005.)
  net3 <- ifelse(net3=="", NA, net3)
  ns3 <- vector()
  for (i in 1:nrow(net3)) {
    ns3[i] <- length(net3[i,][which(!is.na(net3[i,]))])
  }
  net4 <- cbind(data4$egonet4.SQ001.,data4$egonet4.SQ002., data4$egonet4.SQ003.,data4$egonet4.SQ004., data4$egonet4.SQ005.)
  net4 <- ifelse(net4=="", NA, net4)
  ns4 <- vector()
  for (i in 1:nrow(net4)) {
    ns4[i] <- length(net4[i,][which(!is.na(net4[i,]))])
  }
}

# construct the matching matrices list for egonet1-2
matchingList <- list()
for (i in 1:length(alterL)) {
  matchingL <- list()
  matchingL[[1]] <- cbind(data4$matching1N1.SQ001_SQ001.[i],data4$matching1N1.SQ002_SQ001.[i],data4$matching1N1.SQ003_SQ001.[i],data4$matching1N1.SQ004_SQ001.[i],data4$matching1N1.SQ005_SQ001.[i])
  matchingL[[2]]<- rbind(
    cbind(data4$matching1N2.SQ001_SQ001.[i], data4$matching1N2.SQ002_SQ001.[i], data4$matching1N2.SQ003_SQ001.[i], data4$matching1N2.SQ004_SQ001.[i], data4$matching1N2.SQ005_SQ001.[i]),
    cbind(data4$matching1N2.SQ001_SQ002.[i], data4$matching1N2.SQ002_SQ002.[i], data4$matching1N2.SQ003_SQ002.[i], data4$matching1N2.SQ004_SQ002.[i], data4$matching1N2.SQ005_SQ002.[i]))
  matchingL[[3]]<- rbind(
    cbind(data4$matching1N3.SQ001_SQ001.[i], data4$matching1N3.SQ002_SQ001.[i], data4$matching1N3.SQ003_SQ001.[i], data4$matching1N3.SQ004_SQ001.[i], data4$matching1N3.SQ005_SQ001.[i]),
    cbind(data4$matching1N3.SQ001_SQ002.[i], data4$matching1N3.SQ002_SQ002.[i], data4$matching1N3.SQ003_SQ002.[i], data4$matching1N3.SQ004_SQ002.[i], data4$matching1N3.SQ005_SQ002.[i]),
    cbind(data4$matching1N3.SQ001_SQ003.[i], data4$matching1N3.SQ002_SQ003.[i], data4$matching1N3.SQ003_SQ003.[i], data4$matching1N3.SQ004_SQ003.[i], data4$matching1N3.SQ005_SQ003.[i]))
  matchingL[[4]]<- rbind(
    cbind(data4$matching1N4.SQ001_SQ001.[i], data4$matching1N4.SQ002_SQ001.[i], data4$matching1N4.SQ003_SQ001.[i], data4$matching1N4.SQ004_SQ001.[i], data4$matching1N4.SQ005_SQ001.[i]),
    cbind(data4$matching1N4.SQ001_SQ002.[i], data4$matching1N4.SQ002_SQ002.[i], data4$matching1N4.SQ003_SQ002.[i], data4$matching1N4.SQ004_SQ002.[i], data4$matching1N4.SQ005_SQ002.[i]),
    cbind(data4$matching1N4.SQ001_SQ003.[i], data4$matching1N4.SQ002_SQ003.[i], data4$matching1N4.SQ003_SQ003.[i], data4$matching1N4.SQ004_SQ003.[i], data4$matching1N4.SQ005_SQ003.[i]),
    cbind(data4$matching1N4.SQ001_SQ004.[i], data4$matching1N4.SQ002_SQ004.[i], data4$matching1N4.SQ003_SQ004.[i], data4$matching1N4.SQ004_SQ004.[i], data4$matching1N4.SQ005_SQ004.[i]))
  matchingL[[5]]<- rbind(
    cbind(data4$matching1N5.SQ001_SQ001.[i], data4$matching1N5.SQ002_SQ001.[i], data4$matching1N5.SQ003_SQ001.[i], data4$matching1N5.SQ004_SQ001.[i], data4$matching1N5.SQ005_SQ001.[i]),
    cbind(data4$matching1N5.SQ001_SQ002.[i], data4$matching1N5.SQ002_SQ002.[i], data4$matching1N5.SQ003_SQ002.[i], data4$matching1N5.SQ004_SQ002.[i], data4$matching1N5.SQ005_SQ002.[i]),
    cbind(data4$matching1N5.SQ001_SQ003.[i], data4$matching1N5.SQ002_SQ003.[i], data4$matching1N5.SQ003_SQ003.[i], data4$matching1N5.SQ004_SQ003.[i], data4$matching1N5.SQ005_SQ003.[i]),
    cbind(data4$matching1N5.SQ001_SQ004.[i], data4$matching1N5.SQ002_SQ004.[i], data4$matching1N5.SQ003_SQ004.[i], data4$matching1N5.SQ004_SQ004.[i], data4$matching1N5.SQ005_SQ004.[i]),
    cbind(data4$matching1N5.SQ001_SQ005.[i], data4$matching1N5.SQ002_SQ005.[i], data4$matching1N5.SQ003_SQ005.[i], data4$matching1N5.SQ004_SQ005.[i], data4$matching1N5.SQ005_SQ005.[i]))
  matchingList[[i]] <- matchingL
} # so... matchingL[[1]][[5]] is matchingmatrix 5 (i.e., 5 alters named in egonet2) for ego 1

# the combination of the matching matrices and the netsizes for ego allows me to match the names myself.
for (i in 1:length(matchingList)) {     # for ego i
  mL <- matchingList[[i]]               # get the matching list
  ns <- ns2[[i]]                        # get the size of egonet2
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # retrieve the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net2[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name2[which(alterL[[i]]$alterid==matched[,2])] <- net[matched[,1]]
    }
  }
}#ignore warning

# again, make a matching list for the second matching matrices
# (i.e., matching egonet3 alters to prev. alters);
matchingList2 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching2L <- list()
  matching2L[[1]] <- cbind(data4$matching2N1.SQ001_SQ001.[i],data4$matching2N1.SQ002_SQ001.[i],data4$matching2N1.SQ003_SQ001.[i],data4$matching2N1.SQ004_SQ001.[i],data4$matching2N1.SQ005_SQ001.[i],data4$matching2N1.SQ006_SQ001.[i],data4$matching2N1.SQ007_SQ001.[i],data4$matching2N1.SQ008_SQ001.[i],data4$matching2N1.SQ009_SQ001.[i],data4$matching2N1.SQ010_SQ001.[i])
  matching2L[[2]] <- rbind(
    cbind(data4$matching2N2.SQ001_SQ001.[i],data4$matching2N2.SQ002_SQ001.[i],data4$matching2N2.SQ003_SQ001.[i],data4$matching2N2.SQ004_SQ001.[i],data4$matching2N2.SQ005_SQ001.[i],data4$matching2N2.SQ006_SQ001.[i],data4$matching2N2.SQ007_SQ001.[i],data4$matching2N2.SQ008_SQ001.[i],data4$matching2N2.SQ009_SQ001.[i],data4$matching2N2.SQ010_SQ001.[i]),
    cbind(data4$matching2N2.SQ001_SQ002.[i],data4$matching2N2.SQ002_SQ002.[i],data4$matching2N2.SQ003_SQ002.[i],data4$matching2N2.SQ004_SQ002.[i],data4$matching2N2.SQ005_SQ002.[i],data4$matching2N2.SQ006_SQ002.[i],data4$matching2N2.SQ007_SQ002.[i],data4$matching2N2.SQ008_SQ002.[i],data4$matching2N2.SQ009_SQ002.[i],data4$matching2N2.SQ010_SQ002.[i]))
  matching2L[[3]] <- rbind(
    cbind(data4$matching2N3.SQ001_SQ001.[i],data4$matching2N3.SQ002_SQ001.[i],data4$matching2N3.SQ003_SQ001.[i],data4$matching2N3.SQ004_SQ001.[i],data4$matching2N3.SQ005_SQ001.[i],data4$matching2N3.SQ006_SQ001.[i],data4$matching2N3.SQ007_SQ001.[i],data4$matching2N3.SQ008_SQ001.[i],data4$matching2N3.SQ009_SQ001.[i],data4$matching2N3.SQ010_SQ001.[i]),
    cbind(data4$matching2N3.SQ001_SQ002.[i],data4$matching2N3.SQ002_SQ002.[i],data4$matching2N3.SQ003_SQ002.[i],data4$matching2N3.SQ004_SQ002.[i],data4$matching2N3.SQ005_SQ002.[i],data4$matching2N3.SQ006_SQ002.[i],data4$matching2N3.SQ007_SQ002.[i],data4$matching2N3.SQ008_SQ002.[i],data4$matching2N3.SQ009_SQ002.[i],data4$matching2N3.SQ010_SQ002.[i]),
    cbind(data4$matching2N3.SQ001_SQ003.[i],data4$matching2N3.SQ002_SQ003.[i],data4$matching2N3.SQ003_SQ003.[i],data4$matching2N3.SQ004_SQ003.[i],data4$matching2N3.SQ005_SQ003.[i],data4$matching2N3.SQ006_SQ003.[i],data4$matching2N3.SQ007_SQ003.[i],data4$matching2N3.SQ008_SQ003.[i],data4$matching2N3.SQ009_SQ003.[i],data4$matching2N3.SQ010_SQ003.[i]))
  matching2L[[4]] <- rbind(
    cbind(data4$matching2N4.SQ001_SQ001.[i],data4$matching2N4.SQ002_SQ001.[i],data4$matching2N4.SQ003_SQ001.[i],data4$matching2N4.SQ004_SQ001.[i],data4$matching2N4.SQ005_SQ001.[i],data4$matching2N4.SQ006_SQ001.[i],data4$matching2N4.SQ007_SQ001.[i],data4$matching2N4.SQ008_SQ001.[i],data4$matching2N4.SQ009_SQ001.[i],data4$matching2N4.SQ010_SQ001.[i]),
    cbind(data4$matching2N4.SQ001_SQ002.[i],data4$matching2N4.SQ002_SQ002.[i],data4$matching2N4.SQ003_SQ002.[i],data4$matching2N4.SQ004_SQ002.[i],data4$matching2N4.SQ005_SQ002.[i],data4$matching2N4.SQ006_SQ002.[i],data4$matching2N4.SQ007_SQ002.[i],data4$matching2N4.SQ008_SQ002.[i],data4$matching2N4.SQ009_SQ002.[i],data4$matching2N4.SQ010_SQ002.[i]),
    cbind(data4$matching2N4.SQ001_SQ003.[i],data4$matching2N4.SQ002_SQ003.[i],data4$matching2N4.SQ003_SQ003.[i],data4$matching2N4.SQ004_SQ003.[i],data4$matching2N4.SQ005_SQ003.[i],data4$matching2N4.SQ006_SQ003.[i],data4$matching2N4.SQ007_SQ003.[i],data4$matching2N4.SQ008_SQ003.[i],data4$matching2N4.SQ009_SQ003.[i],data4$matching2N4.SQ010_SQ003.[i]),
    cbind(data4$matching2N4.SQ001_SQ004.[i],data4$matching2N4.SQ002_SQ004.[i],data4$matching2N4.SQ003_SQ004.[i],data4$matching2N4.SQ004_SQ004.[i],data4$matching2N4.SQ005_SQ004.[i],data4$matching2N4.SQ006_SQ004.[i],data4$matching2N4.SQ007_SQ004.[i],data4$matching2N4.SQ008_SQ004.[i],data4$matching2N4.SQ009_SQ004.[i],data4$matching2N4.SQ010_SQ004.[i]))
  matching2L[[5]] <- rbind(
    cbind(data4$matching2N5.SQ001_SQ001.[i],data4$matching2N5.SQ002_SQ001.[i],data4$matching2N5.SQ003_SQ001.[i],data4$matching2N5.SQ004_SQ001.[i],data4$matching2N5.SQ005_SQ001.[i],data4$matching2N5.SQ006_SQ001.[i],data4$matching2N5.SQ007_SQ001.[i],data4$matching2N5.SQ008_SQ001.[i],data4$matching2N5.SQ009_SQ001.[i],data4$matching2N5.SQ010_SQ001.[i]),
    cbind(data4$matching2N5.SQ001_SQ002.[i],data4$matching2N5.SQ002_SQ002.[i],data4$matching2N5.SQ003_SQ002.[i],data4$matching2N5.SQ004_SQ002.[i],data4$matching2N5.SQ005_SQ002.[i],data4$matching2N5.SQ006_SQ002.[i],data4$matching2N5.SQ007_SQ002.[i],data4$matching2N5.SQ008_SQ002.[i],data4$matching2N5.SQ009_SQ002.[i],data4$matching2N5.SQ010_SQ002.[i]),
    cbind(data4$matching2N5.SQ001_SQ003.[i],data4$matching2N5.SQ002_SQ003.[i],data4$matching2N5.SQ003_SQ003.[i],data4$matching2N5.SQ004_SQ003.[i],data4$matching2N5.SQ005_SQ003.[i],data4$matching2N5.SQ006_SQ003.[i],data4$matching2N5.SQ007_SQ003.[i],data4$matching2N5.SQ008_SQ003.[i],data4$matching2N5.SQ009_SQ003.[i],data4$matching2N5.SQ010_SQ003.[i]),
    cbind(data4$matching2N5.SQ001_SQ004.[i],data4$matching2N5.SQ002_SQ004.[i],data4$matching2N5.SQ003_SQ004.[i],data4$matching2N5.SQ004_SQ004.[i],data4$matching2N5.SQ005_SQ004.[i],data4$matching2N5.SQ006_SQ004.[i],data4$matching2N5.SQ007_SQ004.[i],data4$matching2N5.SQ008_SQ004.[i],data4$matching2N5.SQ009_SQ004.[i],data4$matching2N5.SQ010_SQ004.[i]),
    cbind(data4$matching2N5.SQ001_SQ005.[i],data4$matching2N5.SQ002_SQ005.[i],data4$matching2N5.SQ003_SQ005.[i],data4$matching2N5.SQ004_SQ005.[i],data4$matching2N5.SQ005_SQ005.[i],data4$matching2N5.SQ006_SQ005.[i],data4$matching2N5.SQ007_SQ005.[i],data4$matching2N5.SQ008_SQ005.[i],data4$matching2N5.SQ009_SQ005.[i],data4$matching2N5.SQ010_SQ005.[i]))
  matchingList2[[i]] <- matching2L
}

for (i in 1:length(matchingList2)) {    # for ego i
  mL <- matchingList2[[i]]              # get the matching list 2
  ns <- ns3[[i]]                        # get the size of egonet3
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net3[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name3[matched[,2]] <- net[matched[,1]]
    }
  }
}

# same for matching 3 (i.e., egonet4 with egonets 1-3)
matchingList3 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching3L <- list()
  matching3L[[1]] <- cbind(data4$matching3N1.SQ001_SQ001.[i],data4$matching3N1.SQ002_SQ001.[i],data4$matching3N1.SQ003_SQ001.[i],data4$matching3N1.SQ004_SQ001.[i],data4$matching3N1.SQ005_SQ001.[i],data4$matching3N1.SQ006_SQ001.[i],data4$matching3N1.SQ007_SQ001.[i],data4$matching3N1.SQ008_SQ001.[i],data4$matching3N1.SQ009_SQ001.[i],data4$matching3N1.SQ010_SQ001.[i], data4$matching3N1.SQ011_SQ001.[i], data4$matching3N1.SQ012_SQ001.[i], data4$matching3N1.SQ013_SQ001.[i], data4$matching3N1.SQ014_SQ001.[i], data4$matching3N1.SQ015_SQ001.[i])
  matching3L[[2]] <- rbind(
    cbind(data4$matching3N2.SQ001_SQ001.[i],data4$matching3N2.SQ002_SQ001.[i],data4$matching3N2.SQ003_SQ001.[i],data4$matching3N2.SQ004_SQ001.[i],data4$matching3N2.SQ005_SQ001.[i],data4$matching3N2.SQ006_SQ001.[i],data4$matching3N2.SQ007_SQ001.[i],data4$matching3N2.SQ008_SQ001.[i],data4$matching3N2.SQ009_SQ001.[i],data4$matching3N2.SQ010_SQ001.[i], data4$matching3N2.SQ011_SQ001.[i], data4$matching3N2.SQ012_SQ001.[i], data4$matching3N2.SQ013_SQ001.[i], data4$matching3N2.SQ014_SQ001.[i], data4$matching3N2.SQ015_SQ001.[i]),
    cbind(data4$matching3N2.SQ001_SQ002.[i],data4$matching3N2.SQ002_SQ002.[i],data4$matching3N2.SQ003_SQ002.[i],data4$matching3N2.SQ004_SQ002.[i],data4$matching3N2.SQ005_SQ002.[i],data4$matching3N2.SQ006_SQ002.[i],data4$matching3N2.SQ007_SQ002.[i],data4$matching3N2.SQ008_SQ002.[i],data4$matching3N2.SQ009_SQ002.[i],data4$matching3N2.SQ010_SQ002.[i], data4$matching3N2.SQ011_SQ002.[i], data4$matching3N2.SQ012_SQ002.[i], data4$matching3N2.SQ013_SQ002.[i], data4$matching3N2.SQ014_SQ002.[i], data4$matching3N2.SQ015_SQ002.[i]))
  matching3L[[3]] <- rbind(
    cbind(data4$matching3N3.SQ001_SQ001.[i],data4$matching3N3.SQ002_SQ001.[i],data4$matching3N3.SQ003_SQ001.[i],data4$matching3N3.SQ004_SQ001.[i],data4$matching3N3.SQ005_SQ001.[i],data4$matching3N3.SQ006_SQ001.[i],data4$matching3N3.SQ007_SQ001.[i],data4$matching3N3.SQ008_SQ001.[i],data4$matching3N3.SQ009_SQ001.[i],data4$matching3N3.SQ010_SQ001.[i], data4$matching3N3.SQ011_SQ001.[i], data4$matching3N3.SQ012_SQ001.[i], data4$matching3N3.SQ013_SQ001.[i], data4$matching3N3.SQ014_SQ001.[i], data4$matching3N3.SQ015_SQ001.[i]),
    cbind(data4$matching3N3.SQ001_SQ002.[i],data4$matching3N3.SQ002_SQ002.[i],data4$matching3N3.SQ003_SQ002.[i],data4$matching3N3.SQ004_SQ002.[i],data4$matching3N3.SQ005_SQ002.[i],data4$matching3N3.SQ006_SQ002.[i],data4$matching3N3.SQ007_SQ002.[i],data4$matching3N3.SQ008_SQ002.[i],data4$matching3N3.SQ009_SQ002.[i],data4$matching3N3.SQ010_SQ002.[i], data4$matching3N3.SQ011_SQ002.[i], data4$matching3N3.SQ012_SQ002.[i], data4$matching3N3.SQ013_SQ002.[i], data4$matching3N3.SQ014_SQ002.[i], data4$matching3N3.SQ015_SQ002.[i]),
    cbind(data4$matching3N3.SQ001_SQ003.[i],data4$matching3N3.SQ002_SQ003.[i],data4$matching3N3.SQ003_SQ003.[i],data4$matching3N3.SQ004_SQ003.[i],data4$matching3N3.SQ005_SQ003.[i],data4$matching3N3.SQ006_SQ003.[i],data4$matching3N3.SQ007_SQ003.[i],data4$matching3N3.SQ008_SQ003.[i],data4$matching3N3.SQ009_SQ003.[i],data4$matching3N3.SQ010_SQ003.[i], data4$matching3N3.SQ011_SQ003.[i], data4$matching3N3.SQ012_SQ003.[i], data4$matching3N3.SQ013_SQ003.[i], data4$matching3N3.SQ014_SQ003.[i], data4$matching3N3.SQ015_SQ003.[i]))
  matching3L[[4]] <- rbind(
    cbind(data4$matching3N4.SQ001_SQ001.[i],data4$matching3N4.SQ002_SQ001.[i],data4$matching3N4.SQ003_SQ001.[i],data4$matching3N4.SQ004_SQ001.[i],data4$matching3N4.SQ005_SQ001.[i],data4$matching3N4.SQ006_SQ001.[i],data4$matching3N4.SQ007_SQ001.[i],data4$matching3N4.SQ008_SQ001.[i],data4$matching3N4.SQ009_SQ001.[i],data4$matching3N4.SQ010_SQ001.[i], data4$matching3N4.SQ011_SQ001.[i], data4$matching3N4.SQ012_SQ001.[i], data4$matching3N4.SQ013_SQ001.[i], data4$matching3N4.SQ014_SQ001.[i], data4$matching3N4.SQ015_SQ001.[i]),
    cbind(data4$matching3N4.SQ001_SQ002.[i],data4$matching3N4.SQ002_SQ002.[i],data4$matching3N4.SQ003_SQ002.[i],data4$matching3N4.SQ004_SQ002.[i],data4$matching3N4.SQ005_SQ002.[i],data4$matching3N4.SQ006_SQ002.[i],data4$matching3N4.SQ007_SQ002.[i],data4$matching3N4.SQ008_SQ002.[i],data4$matching3N4.SQ009_SQ002.[i],data4$matching3N4.SQ010_SQ002.[i], data4$matching3N4.SQ011_SQ002.[i], data4$matching3N4.SQ012_SQ002.[i], data4$matching3N4.SQ013_SQ002.[i], data4$matching3N4.SQ014_SQ002.[i], data4$matching3N4.SQ015_SQ002.[i]),
    cbind(data4$matching3N4.SQ001_SQ003.[i],data4$matching3N4.SQ002_SQ003.[i],data4$matching3N4.SQ003_SQ003.[i],data4$matching3N4.SQ004_SQ003.[i],data4$matching3N4.SQ005_SQ003.[i],data4$matching3N4.SQ006_SQ003.[i],data4$matching3N4.SQ007_SQ003.[i],data4$matching3N4.SQ008_SQ003.[i],data4$matching3N4.SQ009_SQ003.[i],data4$matching3N4.SQ010_SQ003.[i], data4$matching3N4.SQ011_SQ003.[i], data4$matching3N4.SQ012_SQ003.[i], data4$matching3N4.SQ013_SQ003.[i], data4$matching3N4.SQ014_SQ003.[i], data4$matching3N4.SQ015_SQ003.[i]),
    cbind(data4$matching3N4.SQ001_SQ003.[i],data4$matching3N4.SQ002_SQ003.[i],data4$matching3N4.SQ003_SQ003.[i],data4$matching3N4.SQ004_SQ003.[i],data4$matching3N4.SQ005_SQ003.[i],data4$matching3N4.SQ006_SQ003.[i],data4$matching3N4.SQ007_SQ003.[i],data4$matching3N4.SQ008_SQ003.[i],data4$matching3N4.SQ009_SQ003.[i],data4$matching3N4.SQ010_SQ003.[i], data4$matching3N4.SQ011_SQ003.[i], data4$matching3N4.SQ012_SQ003.[i], data4$matching3N4.SQ013_SQ003.[i], data4$matching3N4.SQ014_SQ003.[i], data4$matching3N4.SQ015_SQ003.[i]),
    cbind(data4$matching3N4.SQ001_SQ004.[i],data4$matching3N4.SQ002_SQ004.[i],data4$matching3N4.SQ003_SQ004.[i],data4$matching3N4.SQ004_SQ004.[i],data4$matching3N4.SQ005_SQ004.[i],data4$matching3N4.SQ006_SQ004.[i],data4$matching3N4.SQ007_SQ004.[i],data4$matching3N4.SQ008_SQ004.[i],data4$matching3N4.SQ009_SQ004.[i],data4$matching3N4.SQ010_SQ004.[i], data4$matching3N4.SQ011_SQ004.[i], data4$matching3N4.SQ012_SQ004.[i], data4$matching3N4.SQ013_SQ004.[i], data4$matching3N4.SQ014_SQ004.[i], data4$matching3N4.SQ015_SQ004.[i]))
  matching3L[[5]] <- rbind(
    cbind(data4$matching3N5.SQ001_SQ001.[i],data4$matching3N5.SQ002_SQ001.[i],data4$matching3N5.SQ003_SQ001.[i],data4$matching3N5.SQ004_SQ001.[i],data4$matching3N5.SQ005_SQ001.[i],data4$matching3N5.SQ006_SQ001.[i],data4$matching3N5.SQ007_SQ001.[i],data4$matching3N5.SQ008_SQ001.[i],data4$matching3N5.SQ009_SQ001.[i],data4$matching3N5.SQ010_SQ001.[i], data4$matching3N5.SQ011_SQ001.[i], data4$matching3N5.SQ012_SQ001.[i], data4$matching3N5.SQ013_SQ001.[i], data4$matching3N5.SQ014_SQ001.[i], data4$matching3N5.SQ015_SQ001.[i]),
    cbind(data4$matching3N5.SQ001_SQ002.[i],data4$matching3N5.SQ002_SQ002.[i],data4$matching3N5.SQ003_SQ002.[i],data4$matching3N5.SQ004_SQ002.[i],data4$matching3N5.SQ005_SQ002.[i],data4$matching3N5.SQ006_SQ002.[i],data4$matching3N5.SQ007_SQ002.[i],data4$matching3N5.SQ008_SQ002.[i],data4$matching3N5.SQ009_SQ002.[i],data4$matching3N5.SQ010_SQ002.[i], data4$matching3N5.SQ011_SQ002.[i], data4$matching3N5.SQ012_SQ002.[i], data4$matching3N5.SQ013_SQ002.[i], data4$matching3N5.SQ014_SQ002.[i], data4$matching3N5.SQ015_SQ002.[i]),
    cbind(data4$matching3N5.SQ001_SQ003.[i],data4$matching3N5.SQ002_SQ003.[i],data4$matching3N5.SQ003_SQ003.[i],data4$matching3N5.SQ004_SQ003.[i],data4$matching3N5.SQ005_SQ003.[i],data4$matching3N5.SQ006_SQ003.[i],data4$matching3N5.SQ007_SQ003.[i],data4$matching3N5.SQ008_SQ003.[i],data4$matching3N5.SQ009_SQ003.[i],data4$matching3N5.SQ010_SQ003.[i], data4$matching3N5.SQ011_SQ003.[i], data4$matching3N5.SQ012_SQ003.[i], data4$matching3N5.SQ013_SQ003.[i], data4$matching3N5.SQ014_SQ003.[i], data4$matching3N5.SQ015_SQ003.[i]),
    cbind(data4$matching3N5.SQ001_SQ003.[i],data4$matching3N5.SQ002_SQ003.[i],data4$matching3N5.SQ003_SQ003.[i],data4$matching3N5.SQ004_SQ003.[i],data4$matching3N5.SQ005_SQ003.[i],data4$matching3N5.SQ006_SQ003.[i],data4$matching3N5.SQ007_SQ003.[i],data4$matching3N5.SQ008_SQ003.[i],data4$matching3N5.SQ009_SQ003.[i],data4$matching3N5.SQ010_SQ003.[i], data4$matching3N5.SQ011_SQ003.[i], data4$matching3N5.SQ012_SQ003.[i], data4$matching3N5.SQ013_SQ003.[i], data4$matching3N5.SQ014_SQ003.[i], data4$matching3N5.SQ015_SQ003.[i]),
    cbind(data4$matching3N5.SQ001_SQ005.[i],data4$matching3N5.SQ002_SQ005.[i],data4$matching3N5.SQ003_SQ005.[i],data4$matching3N5.SQ004_SQ005.[i],data4$matching3N5.SQ005_SQ005.[i],data4$matching3N5.SQ006_SQ005.[i],data4$matching3N5.SQ007_SQ005.[i],data4$matching3N5.SQ008_SQ005.[i],data4$matching3N5.SQ009_SQ005.[i],data4$matching3N5.SQ010_SQ005.[i], data4$matching3N5.SQ011_SQ005.[i], data4$matching3N5.SQ012_SQ005.[i], data4$matching3N5.SQ013_SQ005.[i], data4$matching3N5.SQ014_SQ005.[i], data4$matching3N5.SQ015_SQ005.[i]))
  matchingList3[[i]] <- matching3L
}

for (i in 1:length(matchingList3)) {    # for ego i
  mL <- matchingList3[[i]]              # get the matching list 2
  ns <- ns4[[i]]                        # get the size of egonet4
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net4[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name4[matched[,2]] <- net[matched[,1]]
    }
  }
}

# make long df with alters in ego,
# and indicators for 4 egonets;
df2 <- data.frame(
  ego=rep(1:length(alterL),each=20),alter=rep(1:20),cdn=NA, study=NA,bff=NA,csn=NA)

for (i in unique(df2$ego)) {  
      for (j in 1:20) { # for alters nested in ego
                 
        # find out if names denoting alter j appear in the 4 egonets
        alter <- unlist(alterL[[i]][j,c(2:5)], use.names = FALSE)
        alter <- alter[!is.na(alter)] # exclude NAs
        
        cdn <- alter %in% net1[i,]
        study <- alter %in% net2[i,]
        bff <- alter %in% net3[i,]
        csn <- alter %in% net4[i,]
        
        # and if so, give alter j score 1 on indicators; 0 otherwise
        df2$cdn[which(df2$ego==i & df2$alter==j)] <- ifelse("TRUE" %in% cdn, 1, 0)
        df2$study[which(df2$ego==i & df2$alter==j)] <- ifelse("TRUE" %in% study, 1, 0)
        df2$bff[which(df2$ego==i & df2$alter==j)] <- ifelse("TRUE" %in% bff, 1, 0)
        df2$csn[which(df2$ego==i & df2$alter==j)] <- ifelse("TRUE" %in% csn, 1, 0)
      }
}

# now that i have, for each alter of ego (including duplicates) at t2,
# the nets to which they belong..
# i continue with the w1-w2 matching matrices

# we already subsetted the matching matrices (in `w1w2`)
for (i in unique(df$ego)) {  # for ego i
  
  matchingL <- vector("list", 20) #pre-allocate empty list of length 15, to store matching matrices
  {
    matchingL[[1]] <- w1w2[i,1:20]
    matchingL[[2]] <- w1w2[i,21:40]
    matchingL[[3]] <- w1w2[i,41:60]
    matchingL[[4]] <- w1w2[i,61:80]
    matchingL[[5]] <- w1w2[i,81:100]
    matchingL[[6]] <- w1w2[i,101:120]
    matchingL[[7]] <- w1w2[i,121:140]
    matchingL[[8]] <- w1w2[i,141:160]
    matchingL[[9]] <- w1w2[i,161:180]
    matchingL[[10]] <- w1w2[i,181:200]
    matchingL[[11]] <- w1w2[i,201:220]
    matchingL[[12]] <- w1w2[i,221:240]
    matchingL[[13]] <- w1w2[i,241:260]
    matchingL[[14]] <- w1w2[i,261:280]
    matchingL[[15]] <- w1w2[i,281:300]
    matchingL[[16]] <- w1w2[i,301:320]
    matchingL[[17]] <- w1w2[i,321:340]
    matchingL[[18]] <- w1w2[i,341:360]
    matchingL[[19]] <- w1w2[i,361:380]
    matchingL[[20]] <- w1w2[i,381:400]
  }
  
  #find the 'right' matching matrix in this list, by taking the one that contains answers
  ind <- NULL
  for (j in seq_along(matchingL)) {
    #check along the sequence of elements j in the matching matrix list if they are non-empty and not NA
    check <- FALSE
    for (col in matchingL[[j]]) {
      if (!all(is.na(col)) && any(nchar(col) > 0)) {
        check <- TRUE
        break  
      }
      }
    if (check) {
      ind <- j
      break  
    }
  }
  
  if(length(ind)>0) {
    # get the  corresponding matrix
    mm <- matchingL[[ind]]
    
    # extract alter ids
    ans <- stringr::str_extract_all(mm,"\\(?[0-9,.]+\\)?") 
    # here, the object refers to the w1-alter j;
    # and the element indicator in the list refers to the w2-alter 
    
    for (j in unique(df$alterid[which(df$ego==i)])) { # for w1-alter j,
      
      # to which row/w2-alter was alter j matched?
      match <- which(ans==j)
      # and in which networks did this w2-alter belong?
      nets <- df2[which(df2$ego==i & df2$alter==match[1]),] #add [1] to match, for the few cases where multiple w2-alters were matched to the same w1-alter (i.e., when ego did not correclty perform match w2 alters to each other.)
    
    if(length(match)>0) { # if j was matched to w2-alters...
      # assign to alter j the networks in which j reappeared
      df$cdn2[which(df$ego==i & df$alterid==j)] <- nets$cdn[1]
      df$study2[which(df$ego==i & df$alterid==j)] <- nets$study[1]
      df$bff2[which(df$ego==i & df$alterid==j)] <- nets$bff[1]
      df$csn2[which(df$ego==i & df$alterid==j)] <- nets$csn[1]
    }
  }
  }
}

# currently; a lot of NAs in the attributes indicating whether alter j was member of the respective networks.
# those are alters that were not renamed, and thus have no 'chance' to re-appear. so, 0s are alters that were once part of a specific network, but re-appeared not in that particular network.
# naturally, for analyses, NAs can be set to 0.

# as a second tie change indicator, i look at whether (un-listed) alters and ego were still in touch
df$frequency.t2 <- NA
df$closeness.t2 <- NA

# subset w2 name interpreters on contact freq. of w1 alters (sq021 - sq040!)
freq <- data4[,c(1176:1195)]
# also closeness
close <- data4[,c(1216:1235)]

# recode into numeric values;
freq <- ifelse(freq=="(Bijna) elke dag",7,
                       ifelse(freq=="1-2 keer per week",6,
                              ifelse(freq=="Aantal keer per maand",5, 
                                     ifelse(freq=="Ong. 1 keer per maand",4, 
                                            ifelse(freq=="Aantal keer per jaar",3,
                                                   ifelse(freq=="Ong. 1 keer per jaar",2,
                                                          ifelse(freq=="Nooit",1,
                                                                      NA   )))))))
close <- ifelse(close=="Heel erg hecht", 4, ifelse(close=="Hecht", 3, ifelse(close=="Enigszins hecht",2, ifelse(close=="Niet hecht", 1, NA))))

for (i in unique(df$ego)) {
  for (j in unique(df$alterid[which(df$ego==i)])) {
    df$frequency.t2[which(df$ego==i & df$alterid==j)] <- freq[i,][!is.na(freq[i,])][j]
    df$closeness.t2[which(df$ego==i & df$alterid==j)] <- close[i,][!is.na(close[i,])][j]
  }
}

# size of each egonet at t2
df$cdn.size2 <- NA
df$study.size2 <- NA
df$bff.size2 <- NA
df$csn.size2 <- NA

for (i in unique(df$ego)) {
  df$cdn.size2[which(df$ego==i)] <- rowSums(cbind(data4$egonet1.SQ001.[i],data4$egonet1.SQ002.[i],data4$egonet1.SQ003.[i],data4$egonet1.SQ004.[i],data4$egonet1.SQ005.[i])!="")
    df$study.size2[which(df$ego==i)] <- rowSums(cbind(data4$egonet2.SQ001.[i],data4$egonet2.SQ002.[i],data4$egonet2.SQ003.[i],data4$egonet2.SQ004.[i],data4$egonet2.SQ005.[i])!="")
    df$bff.size2[which(df$ego==i)] <- rowSums(cbind(data4$egonet3.SQ001.[i],data4$egonet3.SQ002.[i],data4$egonet3.SQ003.[i],data4$egonet3.SQ004.[i],data4$egonet3.SQ005.[i])!="")
    df$csn.size2[which(df$ego==i)] <- rowSums(cbind(data4$egonet4.SQ001.[i],data4$egonet4.SQ002.[i],data4$egonet4.SQ003.[i],data4$egonet4.SQ004.[i],data4$egonet4.SQ005.[i])!="") }

#and density at t2.
df$cdn.density2 <- df$study.density2 <- df$csn.density2 <- df$bff.density2 <- NA

for (i in unique(df$ego)) {
  #a. CDN
  size <- df$cdn.size2[which(df$ego==i)][1]
  #no. possible ties between alters
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  #get no. of observed ties
  #only if ego named at least 2 alters in this name generator
  #because only then i can calculate density
  if(size>1) {
    #get alter-alter adjacency matrices of this particular egonet
    adjacency <- data4[i,c(8:27)]

    #i want the correct ones, given the no. of listed alters in this name generator
    #i list the columns numbers of the variables corresponding to each matching matrix set,
    #and subset corresponding columns in `adjacency`
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
   
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$cdn.density2[which(df$ego==i)] <- obs/pos  }
  
  #b. study
  size <- df$study.size2[which(df$ego==i)][1]
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  if(size>1) {
    adjacency <- data4[i,c(33:52)]
    #reorder columns.... messy!
    adjacency <- adjacency[,c("adj2N2a.SQ001.", "adj2N3a.SQ001.", "adj2N3a.SQ002.", "adj2N3b.SQ001.", "adj2N4a.SQ001.", "adj2N4a.SQ002.",
                       "adj2N4a.SQ003.", "adj2N4b.SQ001.", "adj2N4b.SQ002.", "adj2N4c.SQ001.", "adj2N5a.SQ001.", "adj2N5a.SQ002.",
                       "adj2N5a.SQ003.", "adj2N5a.SQ004.", "adj2N5b.SQ001.", "adj2N5b.SQ002.", "adj2N5b.SQ003.", "adj2N5c.SQ001.",
                       "adj2N5c.SQ002.", "adj2N5d.SQ001.")]
    
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
  
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$study.density2[which(df$ego==i)] <- obs/pos }
  
  #c. friends
  size <- df$bff.size2[which(df$ego==i)][1]
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  if(size>1) {
    adjacency <- data4[i,c(156:175)]
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
    
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$bff.density2[which(df$ego==i)] <- obs/pos }

  #d. sports partners
  size <- df$csn.size2[which(df$ego==i)][1]
  pos <- ifelse(size==2, 1, ifelse(size==3, 3, ifelse(size==4, 6, ifelse(size==5, 10, 0))))
  if(size>1) {
    adjacency <- data4[i,c(401:420)]
    adj <- adjacency[,list(0,1,c(2:4),c(5:10),c(11:20))[size][[1]]]
  
    #count number of ties that ego described as (very) close (vs. not close but no stranger; strangers)
    obs <- length(which(adj=="Hecht"|adj=="Erg hecht"))
    df$csn.density2[which(df$ego==i)] <- obs/pos }
}

#set NAs to 0.
df$cdn.density2[is.na(df$cdn.density2)] <- 0
df$study.density2[is.na(df$study.density2)] <- 0
df$bff.density2[is.na(df$bff.density2)] <- 0
df$csn.density2[is.na(df$csn.density2)] <- 0

#add Wave 2 status
df$statusW2 <- NA
df$statusW2 <- ifelse(df$survive==1, "Maintained", "Dropped")

df_maintained <- df
#fix(df_maintained)
#str(df_maintained)

#last make gender numeric..
df_maintained$alter_gender <- as.numeric(df_maintained$alter_gender)
```

<br>

## wave 2 created

```{r, eval = FALSE}
#create a new alter List
alterL <- vector("list", nrow(data))

# loop over all egos
for ( i in 1:length(alterL)) {
    alterL[[i]] <- data.frame(
      ego_gender = NA, ego_age = NA, ego_educ = NA,
      alterid = 1:20, name1 = NA, name2 = NA, name3 = NA, name4 = NA,
      alter_gender = NA, alter_age = NA, alter_educ=NA,
      same_gender = NA, dif_age = NA, sim_educ = NA)
}

#fill in names based on names_df
for ( i in 1:length(alterL)) {
  alterL[[i]]$name1 <- unlist(df_names[i, ], use.names=FALSE)
}

# replace empty strings with <NA>
for (i in 1:length(alterL)) {
  alterL[[i]]$name1 <- ifelse(alterL[[i]]$name1=="", NA, alterL[[i]]$name1)
}

#matching
{
  net1 <- cbind(data4$egonet1.SQ001.,data4$egonet1.SQ002., data4$egonet1.SQ003.,data4$egonet1.SQ004., data4$egonet1.SQ005.)
  net1 <- ifelse(net1=="", NA, net1)
  ns1 <- vector()
  for (i in 1:nrow(net1)) {
    ns1[i] <- length(net1[i,][which(!is.na(net1[i,]))])
  }
  net2 <- cbind(data4$egonet2.SQ001.,data4$egonet2.SQ002., data4$egonet2.SQ003.,data4$egonet2.SQ004., data4$egonet2.SQ005.)
  net2 <- ifelse(net2=="", NA, net2)
  ns2 <- vector()
  for (i in 1:nrow(net2)) {
    ns2[i] <- length(net2[i,][which(!is.na(net2[i,]))])
  }
  net3 <- cbind(data4$egonet3.SQ001.,data4$egonet3.SQ002., data4$egonet3.SQ003.,data4$egonet3.SQ004., data4$egonet3.SQ005.)
  net3 <- ifelse(net3=="", NA, net3)
  ns3 <- vector()
  for (i in 1:nrow(net3)) {
    ns3[i] <- length(net3[i,][which(!is.na(net3[i,]))])
  }
  net4 <- cbind(data4$egonet4.SQ001.,data4$egonet4.SQ002., data4$egonet4.SQ003.,data4$egonet4.SQ004., data4$egonet4.SQ005.)
  net4 <- ifelse(net4=="", NA, net4)
  ns4 <- vector()
  for (i in 1:nrow(net4)) {
    ns4[i] <- length(net4[i,][which(!is.na(net4[i,]))])
  }
}

matchingList <- list()
for (i in 1:length(alterL)) { # for ego i
  matchingL <- list()
  # make 5 seperate matching matrices. naturally, only 1 is relevant... but i will select that later.
  matchingL[[1]] <- cbind(data4$matching1N1.SQ001_SQ001.[i],data4$matching1N1.SQ002_SQ001.[i],data4$matching1N1.SQ003_SQ001.[i],data4$matching1N1.SQ004_SQ001.[i],data4$matching1N1.SQ005_SQ001.[i])
  matchingL[[2]]<- rbind(
    cbind(data4$matching1N2.SQ001_SQ001.[i], data4$matching1N2.SQ002_SQ001.[i], data4$matching1N2.SQ003_SQ001.[i], data4$matching1N2.SQ004_SQ001.[i], data4$matching1N2.SQ005_SQ001.[i]),
    cbind(data4$matching1N2.SQ001_SQ002.[i], data4$matching1N2.SQ002_SQ002.[i], data4$matching1N2.SQ003_SQ002.[i], data4$matching1N2.SQ004_SQ002.[i], data4$matching1N2.SQ005_SQ002.[i]))
  matchingL[[3]]<- rbind(
    cbind(data4$matching1N3.SQ001_SQ001.[i], data4$matching1N3.SQ002_SQ001.[i], data4$matching1N3.SQ003_SQ001.[i], data4$matching1N3.SQ004_SQ001.[i], data4$matching1N3.SQ005_SQ001.[i]),
    cbind(data4$matching1N3.SQ001_SQ002.[i], data4$matching1N3.SQ002_SQ002.[i], data4$matching1N3.SQ003_SQ002.[i], data4$matching1N3.SQ004_SQ002.[i], data4$matching1N3.SQ005_SQ002.[i]),
    cbind(data4$matching1N3.SQ001_SQ003.[i], data4$matching1N3.SQ002_SQ003.[i], data4$matching1N3.SQ003_SQ003.[i], data4$matching1N3.SQ004_SQ003.[i], data4$matching1N3.SQ005_SQ003.[i]))
  matchingL[[4]]<- rbind(
    cbind(data4$matching1N4.SQ001_SQ001.[i], data4$matching1N4.SQ002_SQ001.[i], data4$matching1N4.SQ003_SQ001.[i], data4$matching1N4.SQ004_SQ001.[i], data4$matching1N4.SQ005_SQ001.[i]),
    cbind(data4$matching1N4.SQ001_SQ002.[i], data4$matching1N4.SQ002_SQ002.[i], data4$matching1N4.SQ003_SQ002.[i], data4$matching1N4.SQ004_SQ002.[i], data4$matching1N4.SQ005_SQ002.[i]),
    cbind(data4$matching1N4.SQ001_SQ003.[i], data4$matching1N4.SQ002_SQ003.[i], data4$matching1N4.SQ003_SQ003.[i], data4$matching1N4.SQ004_SQ003.[i], data4$matching1N4.SQ005_SQ003.[i]),
    cbind(data4$matching1N4.SQ001_SQ004.[i], data4$matching1N4.SQ002_SQ004.[i], data4$matching1N4.SQ003_SQ004.[i], data4$matching1N4.SQ004_SQ004.[i], data4$matching1N4.SQ005_SQ004.[i]))
  matchingL[[5]]<- rbind(
    cbind(data4$matching1N5.SQ001_SQ001.[i], data4$matching1N5.SQ002_SQ001.[i], data4$matching1N5.SQ003_SQ001.[i], data4$matching1N5.SQ004_SQ001.[i], data4$matching1N5.SQ005_SQ001.[i]),
    cbind(data4$matching1N5.SQ001_SQ002.[i], data4$matching1N5.SQ002_SQ002.[i], data4$matching1N5.SQ003_SQ002.[i], data4$matching1N5.SQ004_SQ002.[i], data4$matching1N5.SQ005_SQ002.[i]),
    cbind(data4$matching1N5.SQ001_SQ003.[i], data4$matching1N5.SQ002_SQ003.[i], data4$matching1N5.SQ003_SQ003.[i], data4$matching1N5.SQ004_SQ003.[i], data4$matching1N5.SQ005_SQ003.[i]),
    cbind(data4$matching1N5.SQ001_SQ004.[i], data4$matching1N5.SQ002_SQ004.[i], data4$matching1N5.SQ003_SQ004.[i], data4$matching1N5.SQ004_SQ004.[i], data4$matching1N5.SQ005_SQ004.[i]),
    cbind(data4$matching1N5.SQ001_SQ005.[i], data4$matching1N5.SQ002_SQ005.[i], data4$matching1N5.SQ003_SQ005.[i], data4$matching1N5.SQ004_SQ005.[i], data4$matching1N5.SQ005_SQ005.[i]))
  matchingList[[i]] <- matchingL
}

# the combination of the matching matrices and the netsizes for ego allows me to match the names myself.
for (i in 1:length(matchingList)) {     # for ego i
  mL <- matchingList[[i]]               # get the matching list
  ns <- ns2[[i]]                        # get the size of egonet2
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # retrieve the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net2[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name2[which(alterL[[i]]$alterid==matched[,2])] <- net[matched[,1]]
    }
  }
}

matchingList2 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching2L <- list()
  matching2L[[1]] <- cbind(data4$matching2N1.SQ001_SQ001.[i],data4$matching2N1.SQ002_SQ001.[i],data4$matching2N1.SQ003_SQ001.[i],data4$matching2N1.SQ004_SQ001.[i],data4$matching2N1.SQ005_SQ001.[i],data4$matching2N1.SQ006_SQ001.[i],data4$matching2N1.SQ007_SQ001.[i],data4$matching2N1.SQ008_SQ001.[i],data4$matching2N1.SQ009_SQ001.[i],data4$matching2N1.SQ010_SQ001.[i])
  matching2L[[2]] <- rbind(
    cbind(data4$matching2N2.SQ001_SQ001.[i],data4$matching2N2.SQ002_SQ001.[i],data4$matching2N2.SQ003_SQ001.[i],data4$matching2N2.SQ004_SQ001.[i],data4$matching2N2.SQ005_SQ001.[i],data4$matching2N2.SQ006_SQ001.[i],data4$matching2N2.SQ007_SQ001.[i],data4$matching2N2.SQ008_SQ001.[i],data4$matching2N2.SQ009_SQ001.[i],data4$matching2N2.SQ010_SQ001.[i]),
    cbind(data4$matching2N2.SQ001_SQ002.[i],data4$matching2N2.SQ002_SQ002.[i],data4$matching2N2.SQ003_SQ002.[i],data4$matching2N2.SQ004_SQ002.[i],data4$matching2N2.SQ005_SQ002.[i],data4$matching2N2.SQ006_SQ002.[i],data4$matching2N2.SQ007_SQ002.[i],data4$matching2N2.SQ008_SQ002.[i],data4$matching2N2.SQ009_SQ002.[i],data4$matching2N2.SQ010_SQ002.[i]))
  matching2L[[3]] <- rbind(
    cbind(data4$matching2N3.SQ001_SQ001.[i],data4$matching2N3.SQ002_SQ001.[i],data4$matching2N3.SQ003_SQ001.[i],data4$matching2N3.SQ004_SQ001.[i],data4$matching2N3.SQ005_SQ001.[i],data4$matching2N3.SQ006_SQ001.[i],data4$matching2N3.SQ007_SQ001.[i],data4$matching2N3.SQ008_SQ001.[i],data4$matching2N3.SQ009_SQ001.[i],data4$matching2N3.SQ010_SQ001.[i]),
    cbind(data4$matching2N3.SQ001_SQ002.[i],data4$matching2N3.SQ002_SQ002.[i],data4$matching2N3.SQ003_SQ002.[i],data4$matching2N3.SQ004_SQ002.[i],data4$matching2N3.SQ005_SQ002.[i],data4$matching2N3.SQ006_SQ002.[i],data4$matching2N3.SQ007_SQ002.[i],data4$matching2N3.SQ008_SQ002.[i],data4$matching2N3.SQ009_SQ002.[i],data4$matching2N3.SQ010_SQ002.[i]),
    cbind(data4$matching2N3.SQ001_SQ003.[i],data4$matching2N3.SQ002_SQ003.[i],data4$matching2N3.SQ003_SQ003.[i],data4$matching2N3.SQ004_SQ003.[i],data4$matching2N3.SQ005_SQ003.[i],data4$matching2N3.SQ006_SQ003.[i],data4$matching2N3.SQ007_SQ003.[i],data4$matching2N3.SQ008_SQ003.[i],data4$matching2N3.SQ009_SQ003.[i],data4$matching2N3.SQ010_SQ003.[i]))
  matching2L[[4]] <- rbind(
    cbind(data4$matching2N4.SQ001_SQ001.[i],data4$matching2N4.SQ002_SQ001.[i],data4$matching2N4.SQ003_SQ001.[i],data4$matching2N4.SQ004_SQ001.[i],data4$matching2N4.SQ005_SQ001.[i],data4$matching2N4.SQ006_SQ001.[i],data4$matching2N4.SQ007_SQ001.[i],data4$matching2N4.SQ008_SQ001.[i],data4$matching2N4.SQ009_SQ001.[i],data4$matching2N4.SQ010_SQ001.[i]),
    cbind(data4$matching2N4.SQ001_SQ002.[i],data4$matching2N4.SQ002_SQ002.[i],data4$matching2N4.SQ003_SQ002.[i],data4$matching2N4.SQ004_SQ002.[i],data4$matching2N4.SQ005_SQ002.[i],data4$matching2N4.SQ006_SQ002.[i],data4$matching2N4.SQ007_SQ002.[i],data4$matching2N4.SQ008_SQ002.[i],data4$matching2N4.SQ009_SQ002.[i],data4$matching2N4.SQ010_SQ002.[i]),
    cbind(data4$matching2N4.SQ001_SQ003.[i],data4$matching2N4.SQ002_SQ003.[i],data4$matching2N4.SQ003_SQ003.[i],data4$matching2N4.SQ004_SQ003.[i],data4$matching2N4.SQ005_SQ003.[i],data4$matching2N4.SQ006_SQ003.[i],data4$matching2N4.SQ007_SQ003.[i],data4$matching2N4.SQ008_SQ003.[i],data4$matching2N4.SQ009_SQ003.[i],data4$matching2N4.SQ010_SQ003.[i]),
    cbind(data4$matching2N4.SQ001_SQ004.[i],data4$matching2N4.SQ002_SQ004.[i],data4$matching2N4.SQ003_SQ004.[i],data4$matching2N4.SQ004_SQ004.[i],data4$matching2N4.SQ005_SQ004.[i],data4$matching2N4.SQ006_SQ004.[i],data4$matching2N4.SQ007_SQ004.[i],data4$matching2N4.SQ008_SQ004.[i],data4$matching2N4.SQ009_SQ004.[i],data4$matching2N4.SQ010_SQ004.[i]))
  matching2L[[5]] <- rbind(
    cbind(data4$matching2N5.SQ001_SQ001.[i],data4$matching2N5.SQ002_SQ001.[i],data4$matching2N5.SQ003_SQ001.[i],data4$matching2N5.SQ004_SQ001.[i],data4$matching2N5.SQ005_SQ001.[i],data4$matching2N5.SQ006_SQ001.[i],data4$matching2N5.SQ007_SQ001.[i],data4$matching2N5.SQ008_SQ001.[i],data4$matching2N5.SQ009_SQ001.[i],data4$matching2N5.SQ010_SQ001.[i]),
    cbind(data4$matching2N5.SQ001_SQ002.[i],data4$matching2N5.SQ002_SQ002.[i],data4$matching2N5.SQ003_SQ002.[i],data4$matching2N5.SQ004_SQ002.[i],data4$matching2N5.SQ005_SQ002.[i],data4$matching2N5.SQ006_SQ002.[i],data4$matching2N5.SQ007_SQ002.[i],data4$matching2N5.SQ008_SQ002.[i],data4$matching2N5.SQ009_SQ002.[i],data4$matching2N5.SQ010_SQ002.[i]),
    cbind(data4$matching2N5.SQ001_SQ003.[i],data4$matching2N5.SQ002_SQ003.[i],data4$matching2N5.SQ003_SQ003.[i],data4$matching2N5.SQ004_SQ003.[i],data4$matching2N5.SQ005_SQ003.[i],data4$matching2N5.SQ006_SQ003.[i],data4$matching2N5.SQ007_SQ003.[i],data4$matching2N5.SQ008_SQ003.[i],data4$matching2N5.SQ009_SQ003.[i],data4$matching2N5.SQ010_SQ003.[i]),
    cbind(data4$matching2N5.SQ001_SQ004.[i],data4$matching2N5.SQ002_SQ004.[i],data4$matching2N5.SQ003_SQ004.[i],data4$matching2N5.SQ004_SQ004.[i],data4$matching2N5.SQ005_SQ004.[i],data4$matching2N5.SQ006_SQ004.[i],data4$matching2N5.SQ007_SQ004.[i],data4$matching2N5.SQ008_SQ004.[i],data4$matching2N5.SQ009_SQ004.[i],data4$matching2N5.SQ010_SQ004.[i]),
    cbind(data4$matching2N5.SQ001_SQ005.[i],data4$matching2N5.SQ002_SQ005.[i],data4$matching2N5.SQ003_SQ005.[i],data4$matching2N5.SQ004_SQ005.[i],data4$matching2N5.SQ005_SQ005.[i],data4$matching2N5.SQ006_SQ005.[i],data4$matching2N5.SQ007_SQ005.[i],data4$matching2N5.SQ008_SQ005.[i],data4$matching2N5.SQ009_SQ005.[i],data4$matching2N5.SQ010_SQ005.[i]))
  matchingList2[[i]] <- matching2L
}

for (i in 1:length(matchingList2)) {    # for ego i
  mL <- matchingList2[[i]]              # get the matching list 2
  ns <- ns3[[i]]                        # get the size of egonet3
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net3[i,]
    
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name3[matched[,2]] <- net[matched[,1]]
    }
  }
}

matchingList3 <- list()
for (i in 1:length(alterL)) { # for ego i
  matching3L <- list()
  matching3L[[1]] <- cbind(data4$matching3N1.SQ001_SQ001.[i],data4$matching3N1.SQ002_SQ001.[i],data4$matching3N1.SQ003_SQ001.[i],data4$matching3N1.SQ004_SQ001.[i],data4$matching3N1.SQ005_SQ001.[i],data4$matching3N1.SQ006_SQ001.[i],data4$matching3N1.SQ007_SQ001.[i],data4$matching3N1.SQ008_SQ001.[i],data4$matching3N1.SQ009_SQ001.[i],data4$matching3N1.SQ010_SQ001.[i], data4$matching3N1.SQ011_SQ001.[i], data4$matching3N1.SQ012_SQ001.[i], data4$matching3N1.SQ013_SQ001.[i], data4$matching3N1.SQ014_SQ001.[i], data4$matching3N1.SQ015_SQ001.[i])
  matching3L[[2]] <- rbind(
    cbind(data4$matching3N2.SQ001_SQ001.[i],data4$matching3N2.SQ002_SQ001.[i],data4$matching3N2.SQ003_SQ001.[i],data4$matching3N2.SQ004_SQ001.[i],data4$matching3N2.SQ005_SQ001.[i],data4$matching3N2.SQ006_SQ001.[i],data4$matching3N2.SQ007_SQ001.[i],data4$matching3N2.SQ008_SQ001.[i],data4$matching3N2.SQ009_SQ001.[i],data4$matching3N2.SQ010_SQ001.[i], data4$matching3N2.SQ011_SQ001.[i], data4$matching3N2.SQ012_SQ001.[i], data4$matching3N2.SQ013_SQ001.[i], data4$matching3N2.SQ014_SQ001.[i], data4$matching3N2.SQ015_SQ001.[i]),
    cbind(data4$matching3N2.SQ001_SQ002.[i],data4$matching3N2.SQ002_SQ002.[i],data4$matching3N2.SQ003_SQ002.[i],data4$matching3N2.SQ004_SQ002.[i],data4$matching3N2.SQ005_SQ002.[i],data4$matching3N2.SQ006_SQ002.[i],data4$matching3N2.SQ007_SQ002.[i],data4$matching3N2.SQ008_SQ002.[i],data4$matching3N2.SQ009_SQ002.[i],data4$matching3N2.SQ010_SQ002.[i], data4$matching3N2.SQ011_SQ002.[i], data4$matching3N2.SQ012_SQ002.[i], data4$matching3N2.SQ013_SQ002.[i], data4$matching3N2.SQ014_SQ002.[i], data4$matching3N2.SQ015_SQ002.[i]))
  matching3L[[3]] <- rbind(
    cbind(data4$matching3N3.SQ001_SQ001.[i],data4$matching3N3.SQ002_SQ001.[i],data4$matching3N3.SQ003_SQ001.[i],data4$matching3N3.SQ004_SQ001.[i],data4$matching3N3.SQ005_SQ001.[i],data4$matching3N3.SQ006_SQ001.[i],data4$matching3N3.SQ007_SQ001.[i],data4$matching3N3.SQ008_SQ001.[i],data4$matching3N3.SQ009_SQ001.[i],data4$matching3N3.SQ010_SQ001.[i], data4$matching3N3.SQ011_SQ001.[i], data4$matching3N3.SQ012_SQ001.[i], data4$matching3N3.SQ013_SQ001.[i], data4$matching3N3.SQ014_SQ001.[i], data4$matching3N3.SQ015_SQ001.[i]),
    cbind(data4$matching3N3.SQ001_SQ002.[i],data4$matching3N3.SQ002_SQ002.[i],data4$matching3N3.SQ003_SQ002.[i],data4$matching3N3.SQ004_SQ002.[i],data4$matching3N3.SQ005_SQ002.[i],data4$matching3N3.SQ006_SQ002.[i],data4$matching3N3.SQ007_SQ002.[i],data4$matching3N3.SQ008_SQ002.[i],data4$matching3N3.SQ009_SQ002.[i],data4$matching3N3.SQ010_SQ002.[i], data4$matching3N3.SQ011_SQ002.[i], data4$matching3N3.SQ012_SQ002.[i], data4$matching3N3.SQ013_SQ002.[i], data4$matching3N3.SQ014_SQ002.[i], data4$matching3N3.SQ015_SQ002.[i]),
    cbind(data4$matching3N3.SQ001_SQ003.[i],data4$matching3N3.SQ002_SQ003.[i],data4$matching3N3.SQ003_SQ003.[i],data4$matching3N3.SQ004_SQ003.[i],data4$matching3N3.SQ005_SQ003.[i],data4$matching3N3.SQ006_SQ003.[i],data4$matching3N3.SQ007_SQ003.[i],data4$matching3N3.SQ008_SQ003.[i],data4$matching3N3.SQ009_SQ003.[i],data4$matching3N3.SQ010_SQ003.[i], data4$matching3N3.SQ011_SQ003.[i], data4$matching3N3.SQ012_SQ003.[i], data4$matching3N3.SQ013_SQ003.[i], data4$matching3N3.SQ014_SQ003.[i], data4$matching3N3.SQ015_SQ003.[i]))
  matching3L[[4]] <- rbind(
    cbind(data4$matching3N4.SQ001_SQ001.[i],data4$matching3N4.SQ002_SQ001.[i],data4$matching3N4.SQ003_SQ001.[i],data4$matching3N4.SQ004_SQ001.[i],data4$matching3N4.SQ005_SQ001.[i],data4$matching3N4.SQ006_SQ001.[i],data4$matching3N4.SQ007_SQ001.[i],data4$matching3N4.SQ008_SQ001.[i],data4$matching3N4.SQ009_SQ001.[i],data4$matching3N4.SQ010_SQ001.[i], data4$matching3N4.SQ011_SQ001.[i], data4$matching3N4.SQ012_SQ001.[i], data4$matching3N4.SQ013_SQ001.[i], data4$matching3N4.SQ014_SQ001.[i], data4$matching3N4.SQ015_SQ001.[i]),
    cbind(data4$matching3N4.SQ001_SQ002.[i],data4$matching3N4.SQ002_SQ002.[i],data4$matching3N4.SQ003_SQ002.[i],data4$matching3N4.SQ004_SQ002.[i],data4$matching3N4.SQ005_SQ002.[i],data4$matching3N4.SQ006_SQ002.[i],data4$matching3N4.SQ007_SQ002.[i],data4$matching3N4.SQ008_SQ002.[i],data4$matching3N4.SQ009_SQ002.[i],data4$matching3N4.SQ010_SQ002.[i], data4$matching3N4.SQ011_SQ002.[i], data4$matching3N4.SQ012_SQ002.[i], data4$matching3N4.SQ013_SQ002.[i], data4$matching3N4.SQ014_SQ002.[i], data4$matching3N4.SQ015_SQ002.[i]),
    cbind(data4$matching3N4.SQ001_SQ003.[i],data4$matching3N4.SQ002_SQ003.[i],data4$matching3N4.SQ003_SQ003.[i],data4$matching3N4.SQ004_SQ003.[i],data4$matching3N4.SQ005_SQ003.[i],data4$matching3N4.SQ006_SQ003.[i],data4$matching3N4.SQ007_SQ003.[i],data4$matching3N4.SQ008_SQ003.[i],data4$matching3N4.SQ009_SQ003.[i],data4$matching3N4.SQ010_SQ003.[i], data4$matching3N4.SQ011_SQ003.[i], data4$matching3N4.SQ012_SQ003.[i], data4$matching3N4.SQ013_SQ003.[i], data4$matching3N4.SQ014_SQ003.[i], data4$matching3N4.SQ015_SQ003.[i]),
    cbind(data4$matching3N4.SQ001_SQ003.[i],data4$matching3N4.SQ002_SQ003.[i],data4$matching3N4.SQ003_SQ003.[i],data4$matching3N4.SQ004_SQ003.[i],data4$matching3N4.SQ005_SQ003.[i],data4$matching3N4.SQ006_SQ003.[i],data4$matching3N4.SQ007_SQ003.[i],data4$matching3N4.SQ008_SQ003.[i],data4$matching3N4.SQ009_SQ003.[i],data4$matching3N4.SQ010_SQ003.[i], data4$matching3N4.SQ011_SQ003.[i], data4$matching3N4.SQ012_SQ003.[i], data4$matching3N4.SQ013_SQ003.[i], data4$matching3N4.SQ014_SQ003.[i], data4$matching3N4.SQ015_SQ003.[i]),
    cbind(data4$matching3N4.SQ001_SQ004.[i],data4$matching3N4.SQ002_SQ004.[i],data4$matching3N4.SQ003_SQ004.[i],data4$matching3N4.SQ004_SQ004.[i],data4$matching3N4.SQ005_SQ004.[i],data4$matching3N4.SQ006_SQ004.[i],data4$matching3N4.SQ007_SQ004.[i],data4$matching3N4.SQ008_SQ004.[i],data4$matching3N4.SQ009_SQ004.[i],data4$matching3N4.SQ010_SQ004.[i], data4$matching3N4.SQ011_SQ004.[i], data4$matching3N4.SQ012_SQ004.[i], data4$matching3N4.SQ013_SQ004.[i], data4$matching3N4.SQ014_SQ004.[i], data4$matching3N4.SQ015_SQ004.[i]))
  matching3L[[5]] <- rbind(
    cbind(data4$matching3N5.SQ001_SQ001.[i],data4$matching3N5.SQ002_SQ001.[i],data4$matching3N5.SQ003_SQ001.[i],data4$matching3N5.SQ004_SQ001.[i],data4$matching3N5.SQ005_SQ001.[i],data4$matching3N5.SQ006_SQ001.[i],data4$matching3N5.SQ007_SQ001.[i],data4$matching3N5.SQ008_SQ001.[i],data4$matching3N5.SQ009_SQ001.[i],data4$matching3N5.SQ010_SQ001.[i], data4$matching3N5.SQ011_SQ001.[i], data4$matching3N5.SQ012_SQ001.[i], data4$matching3N5.SQ013_SQ001.[i], data4$matching3N5.SQ014_SQ001.[i], data4$matching3N5.SQ015_SQ001.[i]),
    cbind(data4$matching3N5.SQ001_SQ002.[i],data4$matching3N5.SQ002_SQ002.[i],data4$matching3N5.SQ003_SQ002.[i],data4$matching3N5.SQ004_SQ002.[i],data4$matching3N5.SQ005_SQ002.[i],data4$matching3N5.SQ006_SQ002.[i],data4$matching3N5.SQ007_SQ002.[i],data4$matching3N5.SQ008_SQ002.[i],data4$matching3N5.SQ009_SQ002.[i],data4$matching3N5.SQ010_SQ002.[i], data4$matching3N5.SQ011_SQ002.[i], data4$matching3N5.SQ012_SQ002.[i], data4$matching3N5.SQ013_SQ002.[i], data4$matching3N5.SQ014_SQ002.[i], data4$matching3N5.SQ015_SQ002.[i]),
    cbind(data4$matching3N5.SQ001_SQ003.[i],data4$matching3N5.SQ002_SQ003.[i],data4$matching3N5.SQ003_SQ003.[i],data4$matching3N5.SQ004_SQ003.[i],data4$matching3N5.SQ005_SQ003.[i],data4$matching3N5.SQ006_SQ003.[i],data4$matching3N5.SQ007_SQ003.[i],data4$matching3N5.SQ008_SQ003.[i],data4$matching3N5.SQ009_SQ003.[i],data4$matching3N5.SQ010_SQ003.[i], data4$matching3N5.SQ011_SQ003.[i], data4$matching3N5.SQ012_SQ003.[i], data4$matching3N5.SQ013_SQ003.[i], data4$matching3N5.SQ014_SQ003.[i], data4$matching3N5.SQ015_SQ003.[i]),
    cbind(data4$matching3N5.SQ001_SQ003.[i],data4$matching3N5.SQ002_SQ003.[i],data4$matching3N5.SQ003_SQ003.[i],data4$matching3N5.SQ004_SQ003.[i],data4$matching3N5.SQ005_SQ003.[i],data4$matching3N5.SQ006_SQ003.[i],data4$matching3N5.SQ007_SQ003.[i],data4$matching3N5.SQ008_SQ003.[i],data4$matching3N5.SQ009_SQ003.[i],data4$matching3N5.SQ010_SQ003.[i], data4$matching3N5.SQ011_SQ003.[i], data4$matching3N5.SQ012_SQ003.[i], data4$matching3N5.SQ013_SQ003.[i], data4$matching3N5.SQ014_SQ003.[i], data4$matching3N5.SQ015_SQ003.[i]),
    cbind(data4$matching3N5.SQ001_SQ005.[i],data4$matching3N5.SQ002_SQ005.[i],data4$matching3N5.SQ003_SQ005.[i],data4$matching3N5.SQ004_SQ005.[i],data4$matching3N5.SQ005_SQ005.[i],data4$matching3N5.SQ006_SQ005.[i],data4$matching3N5.SQ007_SQ005.[i],data4$matching3N5.SQ008_SQ005.[i],data4$matching3N5.SQ009_SQ005.[i],data4$matching3N5.SQ010_SQ005.[i], data4$matching3N5.SQ011_SQ005.[i], data4$matching3N5.SQ012_SQ005.[i], data4$matching3N5.SQ013_SQ005.[i], data4$matching3N5.SQ014_SQ005.[i], data4$matching3N5.SQ015_SQ005.[i]))
  matchingList3[[i]] <- matching3L
}

for (i in 1:length(matchingList3)) {    # for ego i
  mL <- matchingList3[[i]]              # get the matching list 2
  ns <- ns4[[i]]                        # get the size of egonet4
  if(ns>0) {                            # if ns=0, no matching was done!
    mm <- as.matrix(mL[[ns]])           # and the corresponding matrix
    matched <- which(mm==1, arr.ind=T)  # retrieve array indices
    net <- net4[i,]
    if(length(matched)>0) {             # if matching was performed!
      alterL[[i]]$name4[matched[,2]] <- net[matched[,1]]
    }
  }
}
#while in wave 1, only the unique alters were listed in the gender-name interpreters
#in wave 2, only the NEW alters were listed (since it is a stable characteristic)
#so only the non-matched alters that did not appear in w1
#i asked respondents to 'check' males.

#gender
df_males <- data.frame(p1 = data4$males.SQ001.,p2 = data4$males.SQ002.,p3 = data4$males.SQ003.,p4 = data4$males.SQ004.,p5 = data4$males.SQ005.,p6 = data4$males.SQ006.,p7 = data4$males.SQ007.,p8 = data4$males.SQ008.,p9 = data4$males.SQ009.,p10= data4$males.SQ010.,p11= data4$males.SQ011.,p12= data4$males.SQ012.,p13= data4$males.SQ013.,p14= data4$males.SQ014.,p15= data4$males.SQ015.,p16= data4$males.SQ016.,p17= data4$males.SQ017.,p18= data4$males.SQ018.,p19= data4$males.SQ019.,p20= data4$males.SQ020.)

#kin 
df_kin <- data.frame(p1 = data4$kin.SQ001.,p2 = data4$kin.SQ002.,p3 = data4$kin.SQ003.,p4 = data4$kin.SQ004.,p5 = data4$kin.SQ005.,p6 = data4$kin.SQ006.,p7 = data4$kin.SQ007.,p8 = data4$kin.SQ008.,p9 = data4$kin.SQ009., p10= data4$kin.SQ010., p11= data4$kin.SQ011., p12= data4$kin.SQ012., p13= data4$kin.SQ013., p14= data4$kin.SQ014.,p15= data4$kin.SQ015., p16= data4$kin.SQ016., p17= data4$kin.SQ017., p18= data4$kin.SQ018., p19= data4$kin.SQ019., p20= data4$kin.SQ020.)

#age 
df_age <- data.frame(p1 = data4$age.SQ001.,p2 = data4$age.SQ002.,p3 = data4$age.SQ003.,p4 = data4$age.SQ004.,p5 = data4$age.SQ005.,p6 = data4$age.SQ006.,p7 = data4$age.SQ007.,p8 = data4$age.SQ008.,p9 = data4$age.SQ009., p10= data4$age.SQ010., p11= data4$age.SQ011., p12= data4$age.SQ012., p13= data4$age.SQ013., p14= data4$age.SQ014.,p15= data4$age.SQ015., p16= data4$age.SQ016., p17= data4$age.SQ017., p18= data4$age.SQ018., p19= data4$age.SQ019., p20= data4$age.SQ020.)

#educ 
df_educ <- data.frame(p1 = data4$educ.SQ001.,p2 = data4$educ.SQ002.,p3 = data4$educ.SQ003.,p4 = data4$educ.SQ004.,p5 = data4$educ.SQ005.,p6 = data4$educ.SQ006.,p7 = data4$educ.SQ007.,p8 = data4$educ.SQ008.,p9 = data4$educ.SQ009., p10= data4$educ.SQ010., p11= data4$educ.SQ011., p12= data4$educ.SQ012., p13= data4$educ.SQ013., p14= data4$educ.SQ014.,p15= data4$educ.SQ015., p16= data4$educ.SQ016., p17= data4$educ.SQ017., p18= data4$educ.SQ018., p19= data4$educ.SQ019., p20= data4$educ.SQ020.)

#duration 
df_duration <- data.frame(p1 = data4$duur.SQ001.,p2 = data4$duur.SQ002.,p3 = data4$duur.SQ003.,p4 = data4$duur.SQ004.,p5 = data4$duur.SQ005.,p6 = data4$duur.SQ006.,p7 = data4$duur.SQ007.,p8 = data4$duur.SQ008.,p9 = data4$duur.SQ009.,p10= data4$duur.SQ010.,p11= data4$duur.SQ011.,p12= data4$duur.SQ012.,p13= data4$duur.SQ013.,p14= data4$duur.SQ014.,p15= data4$duur.SQ015.,p16= data4$duur.SQ016.,p17= data4$duur.SQ017.,p18= data4$duur.SQ018.,p19= data4$duur.SQ019.,p20= data4$duur.SQ020.)

#proximity
df_proximity <- data.frame(p1 = data4$prox.SQ001.,p2 = data4$prox.SQ002.,p3 = data4$prox.SQ003.,p4 = data4$prox.SQ004.,p5 = data4$prox.SQ005.,p6 = data4$prox.SQ006.,p7 = data4$prox.SQ007.,p8 = data4$prox.SQ008., p9 = data4$prox.SQ009.,p10= data4$prox.SQ010., p11= data4$prox.SQ011., p12= data4$prox.SQ012., p13= data4$prox.SQ013., p14= data4$prox.SQ014., p15= data4$prox.SQ015., p16= data4$prox.SQ016., p17= data4$prox.SQ017., p18= data4$prox.SQ018., p19= data4$prox.SQ019., p20= data4$prox.SQ020.)

#and dynamic
#communication frequency
df_freq <- data.frame(p1 = data4$freq.SQ001.,p2 = data4$freq.SQ002.,p3 = data4$freq.SQ003.,p4 = data4$freq.SQ004.,p5 = data4$freq.SQ005.,p6 = data4$freq.SQ006.,p7 = data4$freq.SQ007.,p8 = data4$freq.SQ008., p9 = data4$freq.SQ009.,p10= data4$freq.SQ010., p11= data4$freq.SQ011., p12= data4$freq.SQ012., p13= data4$freq.SQ013., p14= data4$freq.SQ014., p15= data4$freq.SQ015., p16= data4$freq.SQ016., p17= data4$freq.SQ017., p18= data4$freq.SQ018., p19= data4$freq.SQ019., p20= data4$freq.SQ020.)

#closeness
df_close <- data.frame(p1 = data4$close.SQ001.,p2 = data4$close.SQ002.,p3 = data4$close.SQ003.,p4 = data4$close.SQ004.,p5 = data4$close.SQ005.,p6 = data4$close.SQ006.,p7 = data4$close.SQ007.,p8 = data4$close.SQ008., p9 = data4$close.SQ009.,p10= data4$close.SQ010., p11= data4$close.SQ011., p12= data4$close.SQ012., p13= data4$close.SQ013., p14= data4$close.SQ014., p15= data4$close.SQ015., p16= data4$close.SQ016., p17= data4$close.SQ017., p18= data4$close.SQ018., p19= data4$close.SQ019., p20= data4$close.SQ020.)

for (i in 1:length(alterL)) {
  
  alterL[[i]]$alter_gender <- ifelse(unlist(df_males[i,], use.names=F)=="Ja", 0, ifelse(unlist(df_males[i,], use.names=F)=="Nee", 1, NA))
  
  alterL[[i]]$alter_age <- 
    ifelse(unlist(df_age[i,], use.names=F)=="Jonger dan 18 jaar", 16, #???
           ifelse(unlist(df_age[i,], use.names=F)=="18 tot 21 jaar", 20,
                  ifelse(unlist(df_age[i,], use.names=F)=="22 tot 25 jaar", 23,
                         ifelse(unlist(df_age[i,], use.names=F)=="26 tot 30 jaar", 28,
                                ifelse(unlist(df_age[i,], use.names=F)=="31 tot 40 jaar", 35,
                                       ifelse(unlist(df_age[i,], use.names=F)=="Ouder dan 40 jaar", 45, #???
                                              ifelse(unlist(df_age[i,], use.names=F)=="Weet ik niet", NA, # i don't know = missing
                                                     unlist(df_age[i,], use.names=F))))))))
  alterL[[i]]$kin <- ifelse(unlist(df_kin[i,], use.names=F)=="Ja", 1, ifelse(unlist(df_kin[i,], use.names=F)=="Nee", 0, ""))
  
  alterL[[i]]$alter_educ <- ifelse(unlist(df_educ[i,],use.names=F)=="lagere school", 1,
                               ifelse(unlist(df_educ[i,],use.names=F)=="vmbo, mavo", 2,
                                      ifelse(unlist(df_educ[i,],use.names=F)=="mbo", 3,
                                         ifelse(unlist(df_educ[i,],use.names=F)=="havo", 4,
                                            ifelse(unlist(df_educ[i,],use.names=F)=="vwo / gymnasium", 5,
                                                 ifelse(unlist(df_educ[i,],use.names=F)=="hbo", 6,
                                                     ifelse(unlist(df_educ[i,],use.names=F)=="universiteit", 7, NA))))))) 
  
  alterL[[i]]$proximity <- ifelse(unlist(df_proximity[i,], use.names=FALSE) == "In hetzelfde huis", "roommate",
                                  ifelse(unlist(df_proximity[i,], use.names = FALSE) == "In dezelfde buurt" |
                                    unlist(df_proximity[i,],use.names=F)=="In dezelfde straat" |
                                    unlist(df_proximity[i,],use.names=F)=="In dezelfde gemeente", "close",
                                    ifelse(unlist(df_proximity[i,], use.names = FALSE) == "In hetzelfde land" |
                                             unlist(df_proximity[i,], use.names = FALSE) == "In een ander land","far", NA)))
  
  
  
  alterL[[i]]$duration <- ifelse(unlist(df_duration[i,],use.names=F)=="Minder dan 1 jaar", 0, 
                               ifelse(unlist(df_duration[i,],use.names=F)=="1 tot 3 jaar", 2,
                                      ifelse(unlist(df_duration[i,],use.names=F)=="4 tot 8 jaar", 6,
                                             ifelse(unlist(df_duration[i,],use.names=F)=="9 tot 15 jaar", 12,
                                                    ifelse(unlist(df_duration[i,],use.names=F)=="Meer dan 15 jaar", 15,NA )))))
  
  alterL[[i]]$frequency.t2 <- ifelse(unlist(df_freq[i,],use.names=F)=="(Bijna) elke dag", 7,
                               ifelse(unlist(df_freq[i,],use.names=F)=="1-2 keer per week",6,
                                      ifelse(unlist(df_freq[i,],use.names=F)=="Aantal keer per maand",5, 
                                         ifelse(unlist(df_freq[i,],use.names=F)=="Ong. 1 keer per maand",4, 
                                            ifelse(unlist(df_freq[i,],use.names=F)=="Aantal keer per jaar",3,
                                                 ifelse(unlist(df_freq[i,],use.names=F)=="Ong. 1 keer per jaar",2,
                                                     ifelse(unlist(df_freq[i,],use.names=F)=="Nooit",1, NA )))))))
  alterL[[i]]$closeness.t2 <- ifelse(unlist(df_close[i,],use.names=F)=="Niet hecht", 1, 
                               ifelse(unlist(df_close[i,],use.names=F)=="Enigszins hecht", 2,
                                      ifelse(unlist(df_close[i,],use.names=F)=="Hecht", 3,
                                             ifelse(unlist(df_close[i,],use.names=F)=="Heel erg hecht", 4, NA ))))
}

#match ego-covars (based on 'df'.) 
for (i in 1:length(alterL)) {
  alterL[[i]]$ego_gender <- df$ego_gender[which(df$ego==1)][1]
  alterL[[i]]$ego_age <- df$ego_age[which(df$ego==1)][1]
  alterL[[i]]$ego_educ <- df$ego_educ[which(df$ego==1)][1]
}

#sameness
for (i in 1:length(alterL))  { # for ego i
  # get attributes of ego
  agei <- alterL[[i]]$ego_age[1]
  genderi <- alterL[[i]]$ego_gender[1]
  edi <- alterL[[i]]$ego_educ[1]
  
  for (j in 1:max(alterL[[i]]$alterid)) { # for alter j
    # calculate "same gender" (0/1)
    genderj <- as.numeric(alterL[[i]]$alter_gender[j]) # get alter j gender
    same <- ifelse(genderi==genderj, 1, 0)
    alterL[[i]]$same_gender[which(alterL[[i]]$alterid==j)] <- same
    
    #same education
    eduj <- alterL[[i]]$alter_educ[j]
    same <- ifelse(eduj==edi, 1, 0)
    alterL[[i]]$sim_educ[which(alterL[[i]]$alterid==j)] <- same
    
    # calculate similarity for age as the absolute difference between alter and ego value
    #get alter j attributes
    agej <- as.numeric(alterL[[i]]$alter_age[j])
    #difference score
    difage <- abs(agei - agej)
    
    # so higher values represent *less* similarity
    if( !is.na (agej) ) { # age similarity only calculable if z_j is known!
        alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- difage
      } else { alterL[[i]]$dif_age[which(alterL[[i]]$alterid==j)] <- NA}
  }
}
  
#in which egonets did altesr appear at t2?
for (i in 1:length(alterL))  { 
  for (j in 1:nrow(alterL[[i]])) {
    
    #get name(s) of j
    alter <- unlist(alterL[[i]][j,c(5:8)], use.names=FALSE)
    alter <- alter[!is.na(alter)] # exclude NAs
    
    #find out alter j appears in the 4 egonets
    cdn <- alter %in% net1[i,]
    study <- alter %in% net2[i,]
    bff <- alter %in% net3[i,]
    csn <- alter %in% net4[i,]
    
    # and if so, give alter j score 1 on indicators; 0 otherwise
    alterL[[i]]$cdn2[j] <- ifelse("TRUE" %in% cdn, 1, 0)
    alterL[[i]]$study2[j] <- ifelse("TRUE" %in% study, 1, 0)
    alterL[[i]]$bff2[j] <- ifelse("TRUE" %in% bff, 1, 0)
    alterL[[i]]$csn2[j] <- ifelse("TRUE" %in% csn, 1, 0)
  }
}

#calculate multiplexity as an alter/tie attribute (i.e., number of *additional* networks j appeared in)
for (i in 1:length(alterL))  {
  for (j in 1:nrow(alterL[[i]])) {
    alterL[[i]]$multiplex.t2[j] <- rowSums(alterL[[i]][j,c(20:23)]) - 1 #minus one to reach a meaningful intercept
  }
}

# i filter out the maintained alters
# by excluding alters with empty strings for gender attribute
for ( i in 1:length(alterL)) {
  alterL[[i]] <- alterL[[i]][which(!is.na(alterL[[i]]$alter_gender) & alterL[[i]]$alter_gender!=""),]
  
    if (nrow(alterL[[i]])>0){ #if no. of created alters > 0
      # replace the alter id: 1 : no. unique alters
      alterL[[i]]$alterid <- 1:nrow(alterL[[i]])
  }
}

#based on this, i make a long dataframe with alters nested in ego.
#first, add an ego_id
for (i in 1:length(alterL)) {
  if(nrow(alterL[[i]]>0)) {
    alterL[[i]]$ego <- i
    alterL[[i]]$respnr <- data$respnr[i]
    }
}

#combine using rbind
df <- do.call(rbind, alterL)

#add network variables; match based on df_maintained
df$cdn.size2 <- df$study.size2 <- df$bff.size2 <- df$csn.size2 <- NA
df$cdn.density2 <- df$study.density2 <- df$bff.density2 <- df$csn.density2 <- NA

for (i in unique(df$ego)) { 
  df$cdn.size2[which(df$ego == i)] <- df_maintained$cdn.size2[which(df_maintained$ego == i)][1]
  df$study.size2[which(df$ego == i)] <- df_maintained$study.size2[which(df_maintained$ego == i)][1]
  df$bff.size2[which(df$ego == i)] <- df_maintained$bff.size2[which(df_maintained$ego == i)][1]
  df$csn.size2[which(df$ego == i)] <- df_maintained$csn.size2[which(df_maintained$ego == i)][1]
  
  df$cdn.density2[which(df$ego == i)] <- df_maintained$cdn.density2[which(df_maintained$ego == i)][1]
  df$study.density2[which(df$ego == i)] <- df_maintained$study.density2[which(df_maintained$ego == i)][1]
  df$bff.density2[which(df$ego == i)] <- df_maintained$bff.density2[which(df_maintained$ego == i)][1]
  df$csn.density2[which(df$ego == i)] <- df_maintained$csn.density2[which(df_maintained$ego == i)][1]
}

df$statusW2 <- "Created"
df_created <- df

```



<br>

## wave 2 -> wave 3

<br>

## aggregate network info to ego

<br>

---

# university sports center data

<br>

---

# References
